

```{r}
#| include: false

# Importing packaegs, functions declaring globals
source("R/packages.R")
source("R/utils.R")
source("R/globals.R")
source("R/functions.R")
source("R/specific_functions.R") # Preparing specialized (non-generic) functions
source("R/viz_functions.R")

# Select country:
#COUNTRY <- params$country
COUNTRY <- "Indonesia"
CITY <- CITIES[[COUNTRY]]

# Preparing enumeration data and weights 
source("R/0_weights.R")
# Preparing main interview data  
source("R/0_main_data.R")

source("R/weights_out.R")

enum_data <- enum_data %>%
    left_join(weights_cluster, by = c("Initial_block_ID")) %>%
    mutate(fullsample = "All businesses")

# Add check that number of rows in main dataset = number of rows in raw dataset
```

```{r}
#| include: false

# Quantities to summarize fieldwork

N_initial_blocks_sampled = WEIGHT_PARAMS[[COUNTRY]]["n"]
N_initial_blocks_inenum = sum(businesses_percluster$N_business_total_percluster > 0)
N_blocks_w_expansion = sum(blocks_percluster$N_blocks_percluster > 1)
N_blocks_enumerated = sum(blocks_percluster$N_blocks_percluster) 

summary <- get_fieldwork_summary_businesses(enum_data)
N_bs_total = summary["business_total"]
N_bs_elig = summary["business_eligible"]
N_bs_selected = summary["business_selected"]
N_bs_interviewed = summary["business_interviewed"]
N_clusters_w_interviews = sum(businesses_percluster$N_business_interviwed_percluster > 0)
N_clusters_w_zero_businesses = sum(businesses_percluster$N_business_total_percluster == 0)
  

```

## Fieldwork summary

  * Enumeration was completed in `{r} N_initial_blocks_inenum` out of `{r} N_initial_blocks_sampled` initial sampled blocks.
  * `{r} N_blocks_w_expansion` of the `{r} N_initial_blocks_inenum` initial sampled blocks enumerated resulted in expansion to adjacent blocks
  * `{r} N_blocks_enumerated` blocks (including both initial sampled and expansion blocks) were enumerated. 
  * In total, `{r} N_bs_total` business were found during enumeration
  * Of all businesses, `{r} num_and_pct(N_bs_elig, N_bs_total)` were eligible for the study
  * Of eligible businesses, `{r} num_and_pct(N_bs_selected, N_bs_elig)` were selected at random for interview
  * Of selected businesses, `{r} num_and_pct(N_bs_interviewed, N_bs_selected)` were successfully interviewed 
  * Successful interviews originate from `{r} N_clusters_w_interviews` initial sampled blocks

```{r, fig.width = 12, fig.asp = 1}
#| label: fig-fieldwork_map
#| echo: false
#| warning: false
#| fig-cap: "Geographic distribution of enumerated blocks"
#| cap-location: margin

library(sf)
library(raster)

# Read the TIFF raster image
raster_img <- get_raster(COUNTRY)
# Read the GeoJSON file
polygons <- get_sampling_grid(COUNTRY)
boundary <- get_boundary(polygons)

# Prepare block-level data
block_data <- businesses_perblock %>% select(BlockID, N_business_total_percluster) %>% mutate(BlockID = as.character(BlockID))

# Merging in number of enumerated businesses per block 
if (COUNTRY %in% c("Alaska")) {

  block_data <- businesses_perblock %>% select(BlockID, N_business_total_percluster) %>% mutate(BlockID = as.character(BlockID))
  
  polygons <- left_join(polygons, block_data, by = join_by(block_id == BlockID)) %>% 
    filter(N_business_total_percluster >= 0)

  map <- "fill"
  
} else { 
  
  block_data <- businesses_percluster %>% select(Initial_block_ID, N_business_total_percluster) %>% mutate(Initial_block_ID = as.character(Initial_block_ID))
  
  polygons <- left_join(polygons, block_data, by = join_by(block_id == Initial_block_ID)) %>% 
  filter(N_business_total_percluster >= 0)
  
    map <- "size"
    
  }

fig_geo(boundary, polygons, raster_img, COUNTRY, map = map, color_opt = "rocket")


```

## The business landscape 


```{r, fig.width = 12, fig.asp = 0.35}
#| label: fig-nbus_size_and_sector
#| echo: false
#| warning: false
#| fig-cap: "Estimated business population by size and sector"
#| cap-location: margin

# Number of firms by size and sector

indicators <- c("business_total")
groups_l1 <- "business_size_agg2"
groups_l2 <- GROUPS[c("business_sector_agg3")]
  
ests <- compute_summary_clusterlevel_2g(indicators, groups_l1, groups_l2, enum_data, keep = "total")
fig_data <- total_businesses(ests)
title <- total_businesses_title(ests, fig_data)

labels <- list(
  title = str_wrap(title, 80),
  subtitle =  "Businesses (N)",
  yax_ti = NULL,
  xax_ti = NULL,
  caption = SOURCE
)

figparams <- list(
  geom_type = "bar", # One of "bar" or "tile"
  bars = list(width = 0.8, position = "stack", labeltotal = TRUE, labeltotal_ndgy = TRUE,labeltotal_extendmax = TRUE, color = "white"), 
  valuelabels = list(show = TRUE, lab_vjust = 0.5, lab_hjust = 0.5, lab_face = "plain", lab_size = 3.5),
  catlabels = list(show = FALSE), 
  errorbars = list(show = FALSE)
)

palette <- c("#41BBD9", "#CEE5F2", "#FF9F1C")
names(palette) <- c("Services: retail/wholesale trade (re-sale)", "Services: transportation, construction, repair, other", "Manufacturing")

scales <- list(
  fillcolor = list(palette = palette), 
  yaxis = list(limits = c(0, 1), nbreaks = 5, type = "number", expand = c(0,0), droplines = FALSE)
)

legend <- list(
  show = TRUE, 
  title = "Industrial sector", 
  nrows = 1, 
  ncols = 1, 
  reverse = TRUE
)

vars <- list(
  xvar = "business_size_agg2", yvar = "total", fillvar = "group_cat_val"
)

fig_flex(fig_data, vars, facets = NULL, figparams, scales, legend, labels, coord_flip = TRUE)


```


---

```{r, fig.width = 12, fig.asp = 0.35}
#| label: fig-mse_chars
#| echo: false
#| warning: false
#| fig-cap: "MSE sample characteristics"
#| cap-location: margin

indicators <- c("business_total")
groups <- GROUPS[c("business_size_agg2", "business_sector_agg3", "business_premise", "business_registration_status", "resp_owner_str", "resp_sex_str")]

ests <- compute_summary_mainlevel_1g(indicators, groups, data = main_data, weights = "weight_msme_adj", psu = NULL, keep = "total")
fig_data <- sample_chars(ests, groups)

labels <- list(
  title = "Characteristics of Micro and Small Enterprises (MSEs) in study sample",
  subtitle =  "MSEs (%)",
  yax_ti = NULL,
  xax_ti = NULL,
  caption = paste(SOURCE, "Notes: MSEs correspond to businesses with 1-10 employees including the owner")
)

figparams <- list(
  geom_type = "bar", # One of "bar" or "tile"
  bars = list(width = 0.9, position = "stack", color = "white", labeltotal = FALSE), 
  valuelabels = list(show = TRUE, lab_hjust = 0.5, lab_vjust = 0.5, lab_face = "plain", lab_size = 3),
  catlabels = list(show = FALSE), 
  errorbars = list(show = FALSE)
)

palette <- c("#A2C3A4", "#C4F1BE", "#FF9F1C", "#41BBD9", "#CEE5F2", "#BFD3C1", "#A2C3A4", "#C4F1BE", "#CEE5F2", "#FF7B9C", "#C4F1BE","#A2C3A4", "#CEE5F2", "#FF7B9C")
names(palette) <- unique(fig_data$group_cat_val)

scales <- list(
  fillcolor = list(palette = palette), 
  yaxis = list(limits = c(0, 1), nbreaks = 5, type = "percent", expand = NULL, droplines = FALSE)
)

legend <- list(
  show = FALSE, 
  title = NULL, 
  nrows = 1, 
  ncols = 1, 
  reverse = TRUE
)

vars <- list(
  xvar = "group_name", yvar = "share", fillvar = "group_cat_val"
)

fig_flex(fig_data, vars, facets = NULL, figparams, scales, legend, labels, coord_flip = TRUE)



```


---

```{r, fig.width = 12, fig.asp = 0.55}
#| label: fig-mse_sector
#| echo: false
#| warning: false
#| fig-cap: "MSEs by sector of production"
#| cap-location: margin

indicators <- c("business_total")
groups <- GROUPS[c("business_sector_str")]

ests_all <- compute_summary_mainlevel_1g(indicators, groups, data = main_data, weights = "weight_msme_adj", psu = NULL, keep = "total") %>% mutate(subgroup = "All businesses")
ests_men <- compute_summary_mainlevel_1g(indicators, groups, data = main_data %>% filter(resp_sex_men == 1), weights = "weight_msme_adj", psu = NULL, keep = "total") %>% mutate(subgroup = "Men owned\nor managed")
ests_women <- compute_summary_mainlevel_1g(indicators, groups, data = main_data %>% filter(resp_sex_women == 1), weights = "weight_msme_adj", psu = NULL, keep = "total")  %>% mutate(subgroup = "Women owned\nor managed")
  
fig_data <- sample_sector(bind_rows(ests_all, ests_men, ests_women), sector_agg0_to_agg3(main_data))

labels <- list(
  title = "MSEs by sector of production",
  subtitle =  "MSEs (%)",
  yax_ti = NULL,
  xax_ti = NULL,
  caption = paste(SOURCE, "Notes: MSEs correspond to businesses with 1-10 employees including the owner")
)

figparams <- list(
  geom_type = "bar", # One of "bar" or "tile"
  bars = list(width = 0.9, position = "stack", color = "white", labeltotal = FALSE), 
  valuelabels = list(show = FALSE, lab_hjust = 0.5, lab_vjust = 0.5, lab_face = "plain", lab_size = 3),
  catlabels = list(show = FALSE), 
  errorbars = list(show = FALSE)
)

palette <- c("#41BBD9", "#CEE5F2", "#FF9F1C")
names(palette) <- c("Services: trade (re-sale)", "Services: other (eg. transport, construction)", "Manufacturing")

maxy <- roundupN(max(fig_data$share, na.rm = TRUE))

scales <- list(
  fillcolor = list(palette = palette), 
  yaxis = list(limits = c(0, maxy), nbreaks = 5, type = "percent", expand = NULL, droplines = FALSE)
)

legend <- list(
  show = TRUE, 
  title = NULL, 
  nrows = 3, 
  ncols = 1, 
  reverse = TRUE
)

vars <- list(
  xvar = "group_cat_val", yvar = "share", fillvar = "business_sector_agg3"
)

facets <- list(
  type = "wrap", 
  rows = "subgroup", 
  cols = "subgroup",
  nrows = 1, 
  ncols = 1,
  scales = "fixed", 
  drop_row_label = FALSE, 
  drop_col_label = FALSE, 
  add_dividers = TRUE
)

fig_flex(fig_data, vars, facets = facets, figparams, scales, legend, labels, coord_flip = TRUE)

```


---

```{r, fig.width = 12, fig.asp = 0.35}
#| label: fig-mses_productivity
#| echo: false
#| warning: false
#| fig-cap: "MSE revenues and productivity"
#| cap-location: margin

# Firm performance: Monthly revenue and normalized sales per employee
fig_notes <- "Notes: MSEs reported monthly revenue in local currency, these values are converted to USD using June 1 2024 exchange rates obtained from UN treasury data. Daily sales per employee is computed by standardizing revenues across firms using data on the months per year and the hours per week the business is in operation."

indicators <- c("perf_rev_reports", "perf_rev_usd", "perf_revpdypemp_usd")
groups <- GROUPS[c("fullsample", "business_size_agg2", "business_sector_agg3")]

ests <- compute_summary_mainlevel_1g(indicators, groups, data = main_data, weights = "weight_msme_adj", psu = NULL, keep = NULL)

factor_params <- list(
  wrap_sizes = list(indicator_name = 30, indicator_group = 30, group_name = 25, group_cat_val = NULL), 
  reverse_order = list(indicator_name = TRUE, indicator_group = FALSE, group_name = FALSE, group_cat_val = TRUE), 
  order_vars = list(indicator_name = NULL, indicator_group = NULL, group_name = NULL, group_cat_val = NULL)
)

fig_data <- prep_fig_data(ests, factor_params, include_valuelabel = FALSE) %>% 
  mutate(
    mean = ifelse(indicator == "perf_rev_reports", mean*100, median), 
    mean_low = ifelse(indicator == "perf_rev_reports", mean_low*100, median_low), 
    mean_upp = ifelse(indicator == "perf_rev_reports", mean_upp*100, median_upp), 
    indicator_name = fct_inorder(indicator_name), 
    valuelabel = ifelse(indicator %in% c("perf_rev_reports", "perf_rev_usd"), prettyNum(round(mean, 0), big.mark = ","), round(mean, 2))
    )

labels <- list(
  title = "MSE revenues and productivity",
  subtitle = "Median monthly sales and standardized daily sales per worker",
  yax_ti = NULL,
  xax_ti = NULL,
  caption = str_wrap(paste(SOURCE, fig_notes), CAP_WRAP)
)

figparams <- list(
  geom_type = "bar", # One of "bar" or "tile"
  bars = list(width = 0.8, position = "dodge", position_width = 0.9, labeltotal = FALSE, fill = "#CEE5F2", color = "white"), 
  valuelabels = list(show = TRUE, lab_hjust = 1, lab_ndgfcty = 1000, lab_ndgdiry = 1, lab_ndgx = 0.5, lab_face = "plain", lab_size = 3.5), 
  catlabels = list(show = FALSE), 
  errorbars = list(show = FALSE, color = "#2374AB")
)

scales <- list(
  fillcolor = list(palette = NULL), 
  yaxis = list(limits = c(0, 1), nbreaks = 5, type = "number", expand = c(0.1, 0.1), droplines = TRUE)
)

legend <- list(
  show = TRUE, 
  title = NULL, 
  nrows = 1, 
  ncols = 1, 
  reverse = FALSE
)

vars <- list(
  xvar = "group_cat_val", yvar = "mean", fillvar = NULL
)

facets <- list(
  type = "wrap", 
  rows = "group_name", 
  nrows = 1, 
  ncols = 2,
  cols = "indicator_name", 
  scales = "free_x", 
  space = "free", 
  drop_row_label = FALSE, 
  drop_col_label = FALSE, 
  add_dividers = TRUE
)

fig_flex(fig_data, vars, facets, figparams, scales, legend, labels, coord_flip = TRUE)

```


---

```{r, fig.width = 12, fig.asp = 0.45}
#| label: fig-mse_perf_subj
#| echo: false
#| warning: false
#| fig-cap: "Changes in MSE outcomes in past year"
#| cap-location: margin

fig_notes <- c("Notes: The data in this figure is based on the firm owner or manager's own evaluation of changes in sales, the number of employees and investments compared to the same time 12 months ago.")

indicators <- c("perf_sales_up", "perf_sales_same", "perf_sales_down", "perf_emp_up", "perf_emp_same",  "perf_emp_down", "perf_investment", "perf_newservices")       

groups <- GROUPS[c("fullsample", "resp_sex_str")]

ests <- compute_summary_mainlevel_1g(indicators, groups, data = main_data, weights = "weight_msme_adj", psu = NULL, keep = "mean")

factor_params <- list(
  wrap_sizes = list(indicator_name = 40, indicator_group = 40, group_name = 25, group_cat_val = NULL), 
  reverse_order = list(indicator_name = TRUE, indicator_group = FALSE, group_name = FALSE, group_cat_val = FALSE), 
  order_vars = list(indicator_name = NULL, indicator_group = NULL, group_name = NULL, group_cat_val = NULL)
)

fig_data <- prep_fig_data(ests, factor_params)

labels <- list(
  title = "Changes in business outcomes in past year",
  subtitle =  "MSEs (%)",
  yax_ti = NULL,
  xax_ti = NULL,
  caption = str_wrap(paste(SOURCE, fig_notes), CAP_WRAP)
)

figparams <- list(
  geom_type = "bar", # One of "bar" or "tile"
  bars = list(width = 0.9, color = "white", position = "dodge", position_width = 0.5, labeltotal = FALSE), 
  valuelabels = list(show = TRUE, lab_hjust = 0, lab_face = "plain", lab_size = 3.5),
  catlabels = list(show = FALSE), 
  errorbars = list(show = FALSE, color = "#2374AB")
)

palette <- c("grey90", "#FF7B9C", "#CEE5F2")
names(palette) <- c("All businesses", "Women", "Men")  

scales <- list(
  fillcolor = list(palette = palette), 
  yaxis = list(limits = c(0, 1), nbreaks = 4, type = "percent", expand = NULL, droplines = TRUE)
)

legend <- list(
  show = TRUE, 
  title = NULL, 
  nrows = 1, 
  ncols = 1, 
  reverse = FALSE
)

vars <- list(
  xvar = "indicator_name", yvar = "mean", fillvar = "group_cat_val"
)

facets <- list(
  type = "grid", 
  rows = "indicator_group", 
  cols = "group_cat_val", 
  scales = "free_y", 
  space = "free", 
  drop_row_label = FALSE, 
  drop_col_label = FALSE, 
  add_dividers = FALSE
)

fig_flex(fig_data, vars, facets, figparams, scales, legend, labels, coord_flip = TRUE)

```


## The small firm owner

```{r, fig.width = 12, fig.asp = 0.4}
#| label: fig-mses_chars_bygender
#| echo: false
#| warning: false
#| fig-cap: "Gender composition of MSEs by sise and sector"
#| cap-location: margin

indicators <- c("resp_sex_men", "resp_sex_women")
groups <- GROUPS[c("fullsample", "business_premise", "business_size_agg2", "business_sector_agg3")]

ests <- compute_summary_mainlevel_1g(indicators, groups, data = main_data, weights = "weight_msme_adj", psu = NULL, keep = "mean")

factor_params <- list(
  wrap_sizes = list(indicator_name = 40, indicator_group = 40, group_name = 40, group_cat_val = 60), 
  reverse_order = list(indicator_name = FALSE, indicator_group = FALSE, group_name = FALSE, group_cat_val = TRUE), 
  order_vars = list(indicator_name = NULL, indicator_group = NULL, group_name = NULL, group_cat_val = NULL)
)

fig_data <- prep_fig_data(ests, factor_params)

labels <- list(
  title = "Share of men and women MSE owners or managers, by business size, sector and premises",
  subtitle =  "MSEs (%)",
  yax_ti = NULL,
  xax_ti = NULL,
  caption = SOURCE
)

figparams <- list(
  geom_type = "bar", # One of "bar" or "tile"
  bars = list(width = 0.9, position = "stack", position_width = 0.9, labeltotal = FALSE, color = "white"), 
  valuelabels = list(show = TRUE, lab_vjust = 0.5, lab_hjust = 0.5, lab_face = "plain", lab_size = 3),
  catlabels = list(show = FALSE), 
  errorbars = list(show = FALSE, color = "#2374AB")
)

palette <- c("#FF7B9C", "#CEE5F2")
names(palette) <- c("Women", "Men")   

scales <- list(
  fillcolor = list(palette = palette), 
  yaxis = list(limits = c(0, 1), nbreaks = 5, type = "percent", expand = NULL, droplines = FALSE)
)

legend <- list(
  show = TRUE, 
  title = NULL, 
  nrows = 1, 
  ncols = 1, 
  reverse = TRUE
)

vars <- list(
  xvar = "group_cat_val", yvar = "mean", fillvar = "indicator_name"
)

facets <- list(
  type = "grid", 
  rows = "group_name", 
  cols = "indicator_group", 
  scales = "free_y", 
  space = "free", 
  drop_row_label = FALSE, 
  drop_col_label = TRUE, 
  add_dividers = FALSE
)

fig_flex(fig_data, vars, facets, figparams, scales, legend, labels, coord_flip = TRUE)


```


---

```{r, fig.width = 12, fig.asp = 0.45}
#| label: fig-mse_owner_chars
#| echo: false
#| warning: false
#| fig-cap: "MSE owner characteristics"
#| cap-location: margin

indicators <- c("resp_education_agg4_shc_non", "resp_education_agg4_shc_pri", "resp_education_agg4_shc_sec", "resp_education_agg4_shc_trt", 
                 "resp_experience_agg5_shc_1", "resp_experience_agg5_shc_2_5", "resp_experience_agg5_shc_6_10", "resp_experience_agg5_shc_11_20", "resp_experience_agg5_shc_20", 
                "resp_age_agg6_shc_25", "resp_age_agg6_shc_2535", "resp_age_agg6_shc_3545", "resp_age_agg6_shc_4555", "resp_age_agg6_shc_5565", "resp_age_agg6_shc_65")

groups <- GROUPS[c("fullsample", "resp_sex_str")]

ests <- compute_summary_mainlevel_1g(indicators, groups, data = main_data, weights = "weight_msme_adj", psu = NULL, keep = "mean")

factor_params <- list(
  wrap_sizes = list(indicator_name = 80, indicator_group = 40, group_name = 25, group_cat_val = NULL), 
  reverse_order = list(indicator_name = TRUE, indicator_group = FALSE, group_name = FALSE, group_cat_val = FALSE), 
  order_vars = list(indicator_name = NULL, indicator_group = NULL, group_name = NULL, group_cat_val = NULL)
)

fig_data <- prep_fig_data(ests, factor_params)

labels <- list(
  title = "Age, education and experience of MSE owners or managers",
  subtitle =  "Owners or managers (%)",
  yax_ti = NULL,
  xax_ti = NULL,
  caption = SOURCE
)

figparams <- list(
  geom_type = "bar", # One of "bar" or "tile"
  bars = list(width = 0.9, color = "white", position = "dodge", position_width = 0.9, labeltotal = FALSE), 
  valuelabels = list(show = FALSE, lab_hjust = 0, lab_face = "plain", lab_size = 3.5),
  catlabels = list(show = FALSE), 
  errorbars = list(show = FALSE, color = "#2374AB")
)

palette <- c("grey90", "#A2C3A4", "#C4F1BE", "#FF7B9C", "#CEE5F2")
names(palette) <- c("All businesses", "1 person", "2-10 people", "Women", "Men")  

scales <- list(
  fillcolor = list(palette = palette), 
  yaxis = list(limits = c(0, 1), nbreaks = 4, type = "percent", expand = NULL, droplines = TRUE)
)

legend <- list(
  show = TRUE, 
  title = NULL, 
  nrows = 1, 
  ncols = 1, 
  reverse = FALSE
)

vars <- list(
  xvar = "indicator_name", yvar = "mean", fillvar = "group_cat_val"
)

facets <- list(
  type = "grid", 
  rows = "indicator_group", 
  cols = "group_name", 
  scales = "free_y", 
  space = "free", 
  drop_row_label = FALSE, 
  drop_col_label = FALSE, 
  add_dividers = FALSE
)

fig_flex(fig_data, vars, facets, figparams, scales, legend, labels, coord_flip = TRUE)


```


---

```{r, fig.width = 12, fig.asp = 0.6}
#| label: fig-mse_owner_psych
#| echo: false
#| warning: false
#| fig-cap: "Pyschographic characrteristics of SME owners or managers, by gender"
#| cap-location: margin

fig_notes <- c("Notes: Only owners were asked about the motivation for starting the business and the primary goal for the business over the next year. MSEs are classified into one of 3 'psychographic orientations' based on owner responses about motivations, goals and attitude to risk. 'Growth' oriented firms are those with owners who see themsevles as entreprenuers, want to grow the business over the next 12 months and who have a medium to high tolerance for risk. 'Survial' oriented firms are those whose owners started the business due to lack of opportunities or other reasons, whose main goal is to cover costs or leave the business and who have a medium to low tolerance for risk. 'Stability' firms are those who neither meet the criteria for 'Growth' or 'Survival'.")

indicators <- c("resp_motivation_entrep", "resp_motivation_lackopp", "resp_motivation_oth", 
                "resp_maingoal_grow",  "resp_maingoal_stab", "resp_maingoal_leave", 
                "resp_riskapproach_aggr", "resp_riskapproach_calc", "resp_riskapproach_avoid", 
                "resi_resp_attitude_chllng_1", "resi_resp_attitude_chllng_2", "resi_resp_attitude_chllng_3" , "resi_resp_attitude_chllng_4", "resp_psych_segment_shc_grow", "resp_psych_segment_shc_stab", "resp_psych_segment_shc_surv")

groups <- GROUPS[c("fullsample")]

ests <- compute_summary_mainlevel_1g(indicators, groups, data = main_data, weights = "weight_msme_adj", psu = NULL, keep = "mean")

factor_params <- list(
  wrap_sizes = list(indicator_name = 80, indicator_group = 30, group_name = 25, group_cat_val = NULL), 
  reverse_order = list(indicator_name = TRUE, indicator_group = FALSE, group_name = FALSE, group_cat_val = FALSE), 
  order_vars = list(indicator_name = NULL, indicator_group = NULL, group_name = NULL, group_cat_val = NULL)
)

fig_data <- prep_fig_data(ests, factor_params)

labels <- list(
   title = "Pyschographic characteristics of MSE owners or managers",
  subtitle = "MSE owners or managers (%)",
  yax_ti = NULL,
  xax_ti = NULL,
  caption = str_wrap(paste(SOURCE, fig_notes), CAP_WRAP)
)

figparams <- list(
  geom_type = "bar", # One of "bar" or "tile"
  bars = list(width = 0.8, position = "dodge", position_width = 0.9, labeltotal = FALSE, fill = "#CEE5F2", color = "white"), 
  valuelabels = list(show = TRUE, lab_hjust = 0, lab_face = "plain", lab_size = 3.5),
  catlabels = list(show = FALSE), 
  errorbars = list(show = FALSE, color = "#2374AB")
)

scales <- list(
  fillcolor = list(palette = NULL), 
  yaxis = list(limits = c(0, 1), nbreaks = 5, type = "percent", expand = NULL, droplines = TRUE)
)

legend <- list(
  show = TRUE, 
  title = NULL, 
  nrows = 1, 
  ncols = 1, 
  reverse = FALSE
)

vars <- list(
  xvar = "indicator_name", yvar = "mean", fillvar = NULL
)

facets <- list(
  type = "grid", 
  rows = "indicator_group", 
  cols = "group_cat_val", 
  scales = "free_y", 
  space = "free", 
  drop_row_label = FALSE, 
  drop_col_label = TRUE, 
  add_dividers = TRUE
)

fig_flex(fig_data, vars, facets, figparams, scales, legend, labels, coord_flip = TRUE)


```


---

```{r, fig.width = 12, fig.asp = 0.4}
#| label: fig-resp_psyc_corr
#| echo: false
#| warning: false
#| fig-cap: "Correlation between owner's motivations, goals and attitudes to risk"
#| cap-location: margin
#| 
selected_indicators <- c("resp_motivation_entrep", "resp_motivation_lackopp", "resp_motivation_oth",
                            "resp_maingoal_grow", "resp_maingoal_leave", "resp_maingoal_stab",
                            "resp_riskapproach_aggr", "resp_riskapproach_avoid", "resp_riskapproach_calc") 
                         #"resi_resp_attitude_chllng_1", "resi_resp_attitude_chllng_2", "resi_resp_attitude_chllng_3", "resi_resp_attitude_chllng_4")

corr <- gen_corrmatrix(main_data, selected_indicators)

fig_data <- corr_data(corr)

corr_chart(fig_data) + theme(strip.text.y.left = element_text(angle = 0))

```

---

```{r, fig.width = 12, fig.asp = 0.65}
#| label: fig-resp_psyc_mca
#| echo: false
#| warning: false
#| fig-cap: "Correlation between owner's motivations, goals and attitudes to risk"
#| cap-location: margin

mca <- runmca_psych(main_data, showgraph = FALSE)

p1 <- fviz_mca_var(mca, choice = "mca.cor", 
            repel = TRUE, # Avoid text overlapping (slow)
            title = str_wrap("Correlation between goals, motivations and risk attitude with principal dimensions", 50),  
            ggtheme = theme_custom())

p2 <- fviz_mca_var(mca, col.var = "cos2",
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"), 
             repel = TRUE, # Avoid text overlapping
             ggtheme = theme_custom())

# Contributions of rows to dimension 1
p3 <- fviz_contrib(mca, choice = "var", axes = 1, top = 15)
# Contributions of rows to dimension 2
p4 <- fviz_contrib(mca, choice = "var", axes = 2, top = 15)

(p1 + p2) / (p3 + p4)
```

---

```{r, fig.width = 12, fig.asp = 0.55}
#| label: fig-reg_growth_gender
#| echo: false
#| warning: false
#| fig-cap: "Relationship between owner's gender and motivations, goals and attitudes to risk"
#| cap-location: margin

fig_notes <- "Notes: The results shown are based on a linear regression model that measures the effect of gender on several outcomes of interest. The 'unadjusted' model does not include any controls, while the 'adjusted' model includes controls for two variables: years of experience and educational attainment. The regression parameters are used to compute predicted probabilities for male and female business owners with the average years of experience running the business in the sample and with primary-level educational attainment."
  
# Defining regressions
  #depvars <- c("resp_psych_segment_shc_grow", "resp_psych_segment_shc_stab", "resp_psych_segment_shc_surv")
  #depvar_labels <- c("Growth and risk oriented", "Stability oriented", "Survival oriented")
  depvars <- c("resp_motivation_entrep", "resp_maingoal_grow", "resp_riskapproach_aggr", "resp_psych_segment_shc_grow")
  depvar_labels <- c("Identifies as an entrepreneur", "Main goal is to grow the business", "Approach to risk is aggressive ", "Growth and risk oriented")
  names(depvar_labels) <- depvars
  maineffects <- "resp_sex_women"
  effect_labels <- c("(Intercept)" = "Men", INDICATORS[maineffects])
  confounds <- c("resp_experience_c", "resp_education_agg4_shc_non", "resp_education_agg4_shc_sec",  "resp_education_agg4_shc_trt")
    
# Running regressions
ests <- bind_rows(
    map(depvars, model_and_prepfig, maineffects, confounds = NULL, data = main_data, depvar_labels, effect_labels, selected_country = COUNTRY),
    map(depvars, model_and_prepfig, maineffects, confounds = confounds, data = main_data, depvar_labels, effect_labels, selected_country = COUNTRY)
  )

factor_params <- list(
  wrap_sizes = list(depvar_label = 20, effect_label = 15, model_type = 25), 
  reverse_order = list(depvar_label = FALSE, effect_label = FALSE, model_type = FALSE), 
  order_vars = list(depvar_label = NULL, effect_label = NULL, model_type = NULL)
)

fig_data <- prep_reg_data(prep_reg_factors(ests, factor_params, include_valuelabel = FALSE)) %>% 
  mutate(effect_label = ifelse(effect_label == "Gender: Women", "Women", "Men"))

labels <- list(
      title = "Observational estimates of the effect of owner's gender on the orientation of firms",
      subtitle = "", 
      y = "Predicted probability (%)",
      x = NULL,
      caption = str_wrap(paste(SOURCE, fig_notes), CAP_WRAP*1.1)
    )

  barparams <- list(
  bars = list(width = 0.6, color = "grey90"), 
  valuelabels = list(show = FALSE, lab_vjust = 0, lab_hjust = 0, lab_ndgy = 0, lab_ndgx = 0.25, lab_face = "plain", lab_size = 3), 
  arrowlabels = list(show = TRUE, lab_vjust = 0.5, lab_hjust = 0.5, lab_ndgy = 0, lab_ndgx = -0.25,  lab_face = "plain", lab_size = 3), 
    baselinelabel = list(show = TRUE, lab_vjust = 0, lab_hjust = 0.5, lab_ndgy = 0, lab_ndgx = 0,  lab_face = "bold", lab_size = 3.5)
) 

scales <- list(
  y = list(limits = c(0,1), position = "left", nbreaks = 3), 
  x = list(position = "bottom")
)

 facets <- list(type = "grid", cols ="depvar_label", rows = "model_type", scales = "free", space = "free", drop_row_label = FALSE) 
    
 fig_regests(fig_data, labels, facets = facets, barparams, scales, effect_desc = "The difference (in percentage points) between women and men owners on motivation, goals and approach to risk", coord_flip = FALSE)


```


---

```{r, fig.width = 12, fig.asp = 0.35}
#| label: fig-mse_hh_owner
#| echo: false
#| warning: false
#| fig-cap: "MSEs and codependence with owner's household"
#| cap-location: margin

fig_notes <- c("Notes: Only owners were asked (1) whether the formal account used for managing the firms finances and payments is separate from their personal or hosuehold account and (2) the share of total household monthly income that comes from the business. 'Business operations and finances are separate from the household' is a composite indicator to identify businesses that (1) operate outside of the owner's household AND (2) have a formal financial account that is separate from the owner's personal or household account")

indicators <- c("business_premise_shc_1", "resp_pcthhincfrmbus_high", "business_account_separate_v2", "business_hh_separate")

groups <- GROUPS[c("resp_sex_str")]

ests <- compute_summary_mainlevel_1g(indicators, groups, data = main_data %>% filter(resp_type_owner == 1), weights = "weight_msme_adj", psu = NULL, keep = "mean") %>% mutate(indicator_name = ifelse(indicator_name == "Household", "Business operates from household premises", indicator_name))


factor_params <- list(
  wrap_sizes = list(indicator_name = 60, indicator_group = 30, group_name = 25, group_cat_val = NULL), 
  reverse_order = list(indicator_name = TRUE, indicator_group = FALSE, group_name = FALSE, group_cat_val = FALSE), 
  order_vars = list(indicator_name = NULL, indicator_group = NULL, group_name = NULL, group_cat_val = NULL)
)

fig_data <- prep_fig_data(ests, factor_params) 

labels <- list(
  title = "Co-dependence of MSE and the owner's household",
  subtitle =  "MSEs (%)",
  yax_ti = NULL,
  xax_ti = NULL,
  caption = str_wrap(paste(SOURCE, fig_notes), CAP_WRAP)
)

figparams <- list(
  geom_type = "bar", # One of "bar" or "tile"
  bars = list(width = 0.8, position = "dodge", position_width = 0.9, labeltotal = FALSE, fill = "#CEE5F2", color = "white"), 
  valuelabels = list(show = TRUE, lab_hjust = 0, lab_face = "plain", lab_size = 3.5),
  catlabels = list(show = FALSE), 
  errorbars = list(show = FALSE, color = "#2374AB")
)

scales <- list(
  fillcolor = list(palette = NULL), 
  yaxis = list(limits = c(0, 1), nbreaks = 5, type = "percent", expand = NULL, droplines = TRUE)
)

legend <- list(
  show = TRUE, 
  title = NULL, 
  nrows = 1, 
  ncols = 1, 
  reverse = FALSE
)

vars <- list(
  xvar = "indicator_name", yvar = "mean", fillvar = NULL
)

facets <- list(
  type = "grid", 
  rows = "indicator_group", 
  cols = "group_cat_val", 
  scales = "free_y", 
  space = "free", 
  drop_row_label = TRUE, 
  drop_col_label = FALSE, 
  add_dividers = FALSE
)

fig_flex(fig_data, vars, facets, figparams, scales, legend, labels, coord_flip = TRUE)


```

## Digital technology 

```{r, fig.width = 12, fig.asp = 0.55}
#| label: fig-digtech_overview
#| echo: false
#| warning: false
#| fig-cap: "Access to connectivity and devices"
#| cap-location: margin

fig_notes <- "Notes: The digital technology adoption score is a score that counts how many digital technologies are in use by the firm, the score ranges from 0 (no digiital technologies used) to 10 (all ten digital technologies labeled in the figure used)."

indicators <- c("tech_has_device", "tech_has_internet", "tech_uses_website", names(main_data)[str_detect(names(main_data), "^(tech.+).(shc.+)$")], "tech_uses_ai", "tech_uses_digpayments", "tech_uses_digloans", "tech_uses_adoption_score")
groups <- GROUPS[c("fullsample", "business_size_agg2", "business_sector_agg3", "resp_sex_str")]

ests <- compute_summary_mainlevel_1g(indicators, groups, data = main_data, weights = "weight_msme_adj", psu = NULL, keep = "mean")

factor_params <- list(
  wrap_sizes = list(indicator_name = 80, indicator_group = 50, group_name = 25, group_cat_val = 20), 
  reverse_order = list(indicator_name = TRUE, indicator_group = FALSE, group_name = FALSE, group_cat_val = FALSE), 
  order_vars = list(indicator_name = NULL, indicator_group = NULL, group_name = NULL, group_cat_val = NULL)
)

fig_data <- prep_fig_data(ests, factor_params)
fig_data <- tech_adoption_landscape(fig_data, wrap = factor_params[["wrap_sizes"]][["indicator_name"]])

labels <- list(
  title = "Digital technologies: Adoption and frequency of use",
  subtitle =  "MSEs (%)",
  yax_ti = NULL,
  xax_ti = NULL,
  caption =  str_wrap(paste(SOURCE, fig_notes), CAP_WRAP)
)

figparams <- list(
  geom_type = "tile", # One of "bar" or "tile"
  tiles = list(color = "white"), 
  valuelabels = list(show = TRUE, lab_hjust = 0.5, lab_face = "plain", lab_size = 3.5),
  catlabels = list(show = FALSE), 
  errorbars = list(show = FALSE)
)

scales <- list(
  fillcolor = list(palette = "identity", direction = NULL), 
  yaxis = list(limits = c(0, 1), nbreaks = 5, type = "percent", expand = NULL, droplines = TRUE)
)

legend <- list(
  show = FALSE, 
  title = NULL, 
  nrows = 1, 
  ncols = 1, 
  reverse = FALSE
)

vars <- list(
  xvar = "indicator_name", yvar = "group_cat_val", fillvar = "fillcolor"
)

facets <- list(
  type = "grid", 
  rows = "indicator_group", 
  cols = "group_name", 
  scales = "free", 
  space = "free",
  drop_row_label = FALSE, 
  drop_col_label = FALSE, 
  add_dividers = FALSE
)

fig_flex(fig_data, vars, facets, figparams, scales, legend, labels, coord_flip = TRUE) 

```


---

```{r, fig.width = 12, fig.asp = 0.45}
#| label: fig-reg_digtech_drivers
#| echo: false
#| warning: false
#| fig-cap: "Predictors of digital technology adoption"
#| cap-location: margin

fig_notes <- "Notes: The results shown are based on a linear regression model that measures the relationship of several owner and firm-level characteristics with digital technology adoption measured using a score that ranges from 0 to 10 depending on the firm's use of ten distinct technologies. The regression parameters are used to compute predicted probabilities to show the marginal effect of each characteristic on digital technology adoption. Age and experience are mean centered and the effect shown corresponds to an increase in 5 years. The height of 'Baseline' corresponds to the predicted digital technology adoption score for firms run by an owner with mean age, mean experience, with primary-level or less educaitonal attainment."
  
# Defining regressions
  depvars <- c("tech_uses_adoption_score")
  depvar_labels <- INDICATORS[depvars]
  maineffects <- c("resp_sex_women", "resp_age_c_5yi", "resp_experience_c_5yi", "resp_education_agg2_shc_secormore", "resp_motivation_entrep", "resp_maingoal_grow", "resp_riskapproach_aggr", "business_sector_agg3_shc_srv_oth", "business_sector_agg3_shc_mfc")
  effect_labels <- c("(Intercept)" = "Baseline", INDICATORS[maineffects])

# Running regressions
ests <- bind_rows(
    map(depvars, model_and_prepfig, maineffects, confounds = NULL, data = main_data, depvar_labels, effect_labels, selected_country = COUNTRY),
  )


# Preparing figure data
factor_params <- list(
  wrap_sizes = list(depvar_label = 20, effect_label = 70, model_type = 25), 
  reverse_order = list(depvar_label = TRUE, effect_label = TRUE, model_type = FALSE), 
  order_vars = list(depvar_label = NULL, effect_label = NULL, model_type = NULL)
)

fig_data <- prep_reg_data(prep_reg_factors(ests, factor_params, include_valuelabel = FALSE))

 labels <- list(
      title = "Predictors of overall technology adoption",
      subtitle = NULL,
      y = "Predicted technology adoption score [0-10]",
      x = NULL,
      caption = str_wrap(paste(SOURCE, fig_notes), CAP_WRAP*1.2)
    )
 
 barparams <- list(
  bars = list(width = 0.6, color = "grey90"), 
  valuelabels = list(show = FALSE, lab_vjust = 0, lab_hjust = 0, lab_ndgy = 0, lab_ndgx = 0.25, lab_face = "plain", lab_size = 3), 
  arrowlabels = list(show = TRUE, lab_vjust = 0.5, lab_hjust = 0.5, lab_ndgy = 0, lab_ndgx = -0.25,  lab_face = "plain", lab_size = 3), 
    baselinelabel = list(show = TRUE, lab_vjust = 0.5, lab_hjust = 0, lab_ndgy = 0, lab_ndgx = 0,  lab_face = "bold", lab_size = 3.5)
) 

 miny <- round(min(fig_data$fig_data), 2) 
maxy <- round(max(fig_data$fig_data), 2) 
buffer <- (maxy - miny)/100
miny <- miny - buffer*2
if (miny > 0) { miny <- 0 }
maxy <- maxy + buffer*2

scales <- list(
  y = list(limits = c(miny,maxy), position = "right", nbreaks = 5), 
  x = list(txtwrap = 50, position = "bottom")
)

fig_regests(fig_data, labels, facets = NULL, barparams, scales, effect_desc = "The effect of each predictor on technology adoption", coord_flip = TRUE)

```


---

```{r, fig.width = 12, fig.asp = 0.4}
#| label: fig-digtech_usecases
#| echo: false
#| warning: false
#| fig-cap: "Digital technology adoption by use case"
#| cap-location: margin

fig_notes <- "Notes: The functional use-case categories are defined as follows: 'Communicating with customers' includes use of messaging (e.g. Whatsapp) or social media apps (e.g. Facebook); 'Accessing markets' includes use of e-commerce platforms (e.g. Amazon) or a dedicated business website; 'Enterprise operations' includes use of digital applications or software (e.g. for booking, inventory management), including aritifical intelligence; 'Digital payment acceptance' includes use of any in-store POS device that accepts digital customer payments (credit or debit cards, mobile money, QR codes), or online payments. The frequency of use of digital payments acceptance is not available, and corresponds to whether the business has used any means of digital payment acceptance in the past 12 months."

#indicators <- c("tech_cat_none", "tech_uses_messaging", "tech_uses_socialmedia", "tech_uses_website", "tech_uses_ecommerce", "tech_uses_software", "tech_uses_ai", "tech_uses_digpayments", "tech_uses_digloans")

indicators <- c("tech_function_comms", "tech_function_mkts", "tech_function_ops", "tech_function_epay", "tech_function_epay_expos", "tech_function_comms_30da", "tech_function_mkts_30da", "tech_function_ops_30da", 
                "tech_function_comms_7da", "tech_function_mkts_7da", "tech_function_ops_7da")

groups <- GROUPS[c("fullsample", "resp_sex_str")]

ests <- compute_summary_mainlevel_1g(indicators, groups, data = main_data, weights = "weight_msme_adj", psu = NULL, keep = "mean")

factor_params <- list(
  wrap_sizes = list(indicator_name = 60, indicator_group = 40, group_name = 25, group_cat_val = NULL), 
  reverse_order = list(indicator_name = TRUE, indicator_group = FALSE, group_name = FALSE, group_cat_val = FALSE), 
  order_vars = list(indicator_name = NULL, indicator_group = NULL, group_name = NULL, group_cat_val = NULL)
)

fig_data <- prep_fig_data(ests, factor_params)

labels <- list(
  title = "Applications of digital technologies used by MSEs",
  subtitle =  "MSEs (%)",
  yax_ti = NULL,
  xax_ti = NULL,
    caption = str_wrap(paste(SOURCE, fig_notes), CAP_WRAP)
)

figparams <- list(
  geom_type = "bar", # One of "bar" or "tile"
  bars = list(width = 0.8, position = "dodge", position_width = 0.9, labeltotal = FALSE, color = "white"), 
  valuelabels = list(show = FALSE, lab_hjust = 0, lab_face = "plain", lab_size = 3.5),
  catlabels = list(show = FALSE), 
  errorbars = list(show = FALSE, color = "#2374AB")
)

palette <- c("#A2C3A4", "#C4F1BE", "#FF9F1C")
names(palette) <- c("Uses", "30-day active", "7-day active")   

scales <- list(
  fillcolor = list(palette = palette), 
  yaxis = list(limits = c(0, 1), nbreaks = 5, type = "percent", expand = NULL, droplines = TRUE)
)

legend <- list(
  show = TRUE, 
  title = NULL, 
  nrows = 1, 
  ncols = 1, 
  reverse = FALSE
)

vars <- list(
  xvar = "indicator_group", yvar = "mean", fillvar = "indicator_name"
)

facets <- list(
  type = "grid", 
  rows = "indicator_group", 
  cols = "group_cat_val", 
  scales = "free", 
  space = "free", 
  drop_row_label = TRUE, 
  drop_col_label = FALSE, 
  add_dividers = FALSE
)

fig_flex(fig_data, vars, facets, figparams, scales, legend, labels, coord_flip = TRUE)


```


---

```{r, fig.width = 12, fig.asp = 0.4}
#| label: fig-digtech_use_depth
#| echo: false
#| warning: false
#| fig-cap: "Depth of digital technology adoption"
#| cap-location: margin

fig_notes <- "Notes: Four use-cases of digital technology are considered here: 'Communicating with customers', 'Accessing markets', 'Enterprise operations' and 'Digital payment acceptance'. MSEs are classified with respect to whether they use digital technology for any one, any two, any three, all four or none of these use-cases."

indicators <- c("tech_cat_none", "tech_cat_any1", "tech_cat_any2", "tech_cat_any3all4")
groups <- GROUPS[c("fullsample", "business_size_agg2", "resp_sex_str", "resp_psych_segment_agg2")]

ests <- compute_summary_mainlevel_1g(indicators, groups, data = main_data, weights = "weight_msme_adj", psu = NULL, keep = "mean")

factor_params <- list(
  wrap_sizes = list(indicator_name = 60, indicator_group = 40, group_name = 25, group_cat_val = NULL), 
  reverse_order = list(indicator_name = TRUE, indicator_group = FALSE, group_name = FALSE, group_cat_val = FALSE), 
  order_vars = list(indicator_name = NULL, indicator_group = NULL, group_name = NULL, group_cat_val = NULL)
)

fig_data <- prep_fig_data(ests, factor_params)

labels <- list(
  title = "Breadth of digital applications used by MSEs",
  subtitle =  "MSEs (%)",
  yax_ti = NULL,
  xax_ti = NULL,
  caption = str_wrap(paste(SOURCE, fig_notes), CAP_WRAP)
)

figparams <- list(
  geom_type = "bar", # One of "bar" or "tile"
  bars = list(width = 0.8, position = "dodge", position_width = 0.9, labeltotal = FALSE, color = "white"), 
  valuelabels = list(show = FALSE, lab_hjust = 0, lab_face = "plain", lab_size = 3.5),
  catlabels = list(show = FALSE), 
  errorbars = list(show = FALSE, color = "#2374AB")
)

palette <- c("grey90", "#A2C3A4", "#C4F1BE", "#FF7B9C", "#CEE5F2",  "#FF9F1C", "#1768AC")
names(palette) <- c("All businesses", "1 person", "2-10 people", "Women", "Men", "Stability or survival", "Growth")   

scales <- list(
  fillcolor = list(palette = palette), 
  yaxis = list(limits = c(0, 1), nbreaks = 5, type = "percent", expand = NULL, droplines = TRUE)
)

legend <- list(
  show = TRUE, 
  title = NULL, 
  nrows = 1, 
  ncols = 1, 
  reverse = FALSE
)

vars <- list(
  xvar = "indicator_name", yvar = "mean", fillvar = "group_cat_val"
)

facets <- list(
  type = "grid", 
  rows = "indicator_group", 
  cols = "group_name", 
  scales = "free", 
  space = "free", 
  drop_row_label = TRUE, 
  drop_col_label = FALSE, 
  add_dividers = TRUE
)

fig_flex(fig_data, vars, facets, figparams, scales, legend, labels, coord_flip = TRUE)


```


---

```{r, fig.width = 12, fig.asp = 0.55}
#| label: fig-tech_adoptionfactors
#| echo: false
#| warning: false
#| fig-cap: "Digital technology adoption factors"
#| cap-location: margin

fig_notes <- "Notes: The data in this figure pertains to the following 3 questions:(1) What are the factors that encouraged you to adopt and actively use the digital technologies you indicated before? (2) What benefits has the use of digital technologies had on your business? (3) What are the main challenges the business has faced in using digital technologies?. These survey questions were only asked to businesses who reported using any of the following non-financial tehcnologies: messaging apps, social media, e-commerce platforms, software for business operations, a website or artificial intelligence."
  
indicators <- c(names(main_data)[str_detect(names(main_data), "adopfactors")],
                names(main_data)[str_detect(names(main_data), "adopbenefits")], 
                names(main_data)[str_detect(names(main_data), "adopchllng")])

groups <- GROUPS[c("fullsample", "business_size_agg2", "resp_sex_str", "resp_psych_segment_agg2")]

ests <- compute_summary_mainlevel_1g(indicators, groups, data = main_data, weights = "weight_msme_adj", psu = NULL, keep = "mean")

factor_params <- list(
  wrap_sizes = list(indicator_name = 60, indicator_group = 40, group_name = 25, group_cat_val = NULL), 
  reverse_order = list(indicator_name = TRUE, indicator_group = FALSE, group_name = FALSE, group_cat_val = FALSE), 
  order_vars = list(indicator_name = NULL, indicator_group = NULL, group_name = NULL, group_cat_val = NULL)
)

fig_data <- prep_fig_data(ests, factor_params)

labels <- list(
  title = "Non-financial digital technology adoption factors, benefits and challenges",
  subtitle =  "MSEs using digital solutions (%)",
  yax_ti = NULL,
  xax_ti = NULL,
  caption = str_wrap(paste(SOURCE, fig_notes), CAP_WRAP)
)

figparams <- list(
  geom_type = "bar", # One of "bar" or "tile"
  bars = list(width = 0.8, position = "dodge", position_width = 0.9, labeltotal = FALSE, color = "white"), 
  valuelabels = list(show = FALSE, lab_hjust = 0, lab_face = "plain", lab_size = 3.5),
  catlabels = list(show = FALSE), 
  errorbars = list(show = FALSE, color = "#2374AB")
)

palette <- c("grey90", "#A2C3A4", "#C4F1BE", "#FF7B9C", "#CEE5F2",  "#FF9F1C", "#1768AC")
names(palette) <- c("All businesses", "1 person", "2-10 people", "Women", "Men", "Stability or survival", "Growth")   

scales <- list(
  fillcolor = list(palette = palette), 
  yaxis = list(limits = c(0, 1), nbreaks = 5, type = "percent", expand = NULL, droplines = TRUE)
)

legend <- list(
  show = TRUE, 
  title = NULL, 
  nrows = 1, 
  ncols = 1, 
  reverse = FALSE
)

vars <- list(
  xvar = "indicator_name", yvar = "mean", fillvar = "group_cat_val"
)

facets <- list(
  type = "grid", 
  rows = "indicator_group", 
  cols = "group_name", 
  scales = "free", 
  space = "free", 
  drop_row_label = FALSE, 
  drop_col_label = FALSE, 
  add_dividers = TRUE
)

fig_flex(fig_data, vars, facets, figparams, scales, legend, labels, coord_flip = TRUE) + theme(axis.text.x = element_text(size = 9))


```

--- 

```{r, fig.width = 12, fig.asp = 0.5}
#| label: fig-reg_revprhr_internet
#| echo: false
#| warning: false
#| fig-cap: "Relationship between internet-connectivity and firm-level labor productivity"
#| cap-location: margin

fig_notes <- "Notes: The results shown are based on a linear regression model that measures the effect of digital technology adoption on firm labor productivity. The 'unadjusted' model does not include any controls, while the 'adjusted' model includes controls for two variables: years of experience and educational attainment. An additional adjusted model controls for experience, education and psychological characteristics of the owner related to motivation, growth orientation and risk tolerance. The regression parameters are used to compute predicted probabilities to show the marginal effect of internet connectivity on productivity. The height of 'Baseline' corresponds to the predicted productivity for firms run by an owner with mean years of experience, and secondary-level educaitonal attainment."
  
# Defining regressions
  depvars <- c("perf_revpdypemp_usd_log")
  depvar_labels <- INDICATORS[depvars]
  maineffects <- c("tech_has_internet")
  effect_labels <- c("(Intercept)" = "No internet connection", INDICATORS[maineffects])
  confounds <- c("resp_experience_c", "resp_education_agg4_shc_non", "resp_education_agg4_shc_pri",  "resp_education_agg4_shc_trt")
  confounds2 <- c("resp_experience_c", "resp_education_agg4_shc_non", "resp_education_agg4_shc_pri",  "resp_education_agg4_shc_trt", "psych_mca_dim1", "psych_mca_dim2")
  
# Running regressions
ests <- bind_rows(
    map(depvars, model_and_prepfig, maineffects, confounds = NULL, data = main_data, depvar_labels, effect_labels, selected_country = COUNTRY,depvarlog = TRUE),
    map(depvars, model_and_prepfig, maineffects, confounds, data = main_data, depvar_labels, effect_labels, selected_country = COUNTRY, depvarlog = TRUE), 
    map(depvars, model_and_prepfig, maineffects, confounds2, data = main_data, depvar_labels, effect_labels, selected_country = COUNTRY, depvarlog = TRUE, model_type_override = "Model: Adjusted (+ pyschographics)") 
  ) %>% mutate(effect_label = str_replace(effect_label, ": Has", ""))
    
factor_params <- list(
  wrap_sizes = list(depvar_label = 20, effect_label = 10, model_type = 25), 
  reverse_order = list(depvar_label = TRUE, effect_label = FALSE, model_type = FALSE), 
  order_vars = list(depvar_label = NULL, effect_label = NULL, model_type = NULL)
)

fig_data <- prep_reg_data(prep_reg_factors(ests, factor_params, include_valuelabel = FALSE), depvarlog = TRUE) %>% 
  mutate(depvar_label = "Predicted daily sales\nper worker (Current USD)")

 labels <- list(
      title = "Observational estimates of the effect of internet connectivity on labor productivity",
      subtitle = "", 
      y = NULL,
      x = NULL,
      caption = str_wrap(paste(SOURCE, fig_notes), CAP_WRAP*1.2)
    )

  barparams <- list(
  bars = list(width = 0.6, color = "grey90"), 
  valuelabels = list(show = FALSE, lab_vjust = 0, lab_hjust = 0, lab_ndgy = 0, lab_ndgx = 0.25, lab_face = "plain", lab_size = 3), 
  arrowlabels = list(show = TRUE, lab_vjust = 0.5, lab_hjust = 0.5, lab_ndgy = 0, lab_ndgx = -0.15,  lab_face = "plain", lab_size = 3),
  baselinelabel = list(show = TRUE, lab_vjust = 0, lab_hjust = 0.5, lab_ndgy = 0, lab_ndgx = 0,  lab_face = "bold", lab_size = 3.5)
) 


miny <- round(min(fig_data$fig_data), 2) 
maxy <- round(max(fig_data$fig_data), 2) 
buffer <- (maxy - miny)/100
miny <- miny - buffer*2
if (miny > 0) { miny <- 0 }
maxy <- maxy + buffer*2

scales <- list(
  y = list(limits = c(miny,maxy), position = "left", nbreaks = 3), 
  x = list(position = "bottom")
)

 facets <- list(type = "grid", rows ="depvar_label", cols = "model_type", scales = "free", space = "free", drop_row_label = FALSE) 
    
 fig_regests(fig_data, labels, facets = facets, barparams, scales, effect_desc = "The effect of an internet connection on labor productivity", coord_flip = FALSE)


```

--- 

```{r, fig.width = 12, fig.asp = 0.5}
#| label: fig-reg_revprhr_digitaladoption
#| echo: false
#| warning: false
#| fig-cap: "Relationship between digital technology and firm-level labor productivity"
#| cap-location: margin

fig_notes <- "Notes: The results shown are based on a linear regression model that measures the effect of digital technology adoption on firm labor productivity. The 'unadjusted' model does not include any controls, while the 'adjusted' model includes controls for two variables: years of experience and educational attainment. An additional adjusted model controls for experience, education and psychological characteristics of the owner related to motivation, growth orientation and risk tolerance. The regression parameters are used to compute predicted probabilities to show the marginal effect of digital technology on productivity. The height of 'Baseline' corresponds to the predicted productivity for firms run by an owner with mean years of experience, and secondary-level educaitonal attainment."
  
# Defining regressions
  depvars <- c("perf_revpdypemp_usd_log")
  depvar_labels <- INDICATORS[depvars]
  maineffects <- c("tech_uses_adoption_score_c")
  effect_labels <- c("(Intercept)" = "Baseline", INDICATORS[maineffects])
  confounds <- c("resp_experience_c", "resp_education_agg4_shc_non", "resp_education_agg4_shc_pri",  "resp_education_agg4_shc_trt")
  confounds2 <- c("resp_experience_c", "resp_education_agg4_shc_non", "resp_education_agg4_shc_pri",  "resp_education_agg4_shc_trt", "psych_mca_dim1", "psych_mca_dim2")
  
# Running regressions
ests <- bind_rows(
    map(depvars, model_and_prepfig, maineffects, confounds = NULL, data = main_data, depvar_labels, effect_labels, selected_country = COUNTRY, depvarlog = TRUE),
    map(depvars, model_and_prepfig, maineffects, confounds, data = main_data, depvar_labels, effect_labels, selected_country = COUNTRY, depvarlog = TRUE), 
    map(depvars, model_and_prepfig, maineffects, confounds2, data = main_data, depvar_labels, effect_labels, selected_country = COUNTRY, depvarlog = TRUE, model_type_override = "Model: Adjusted (+ pyschographics)") 
  )
    
factor_params <- list(
  wrap_sizes = list(depvar_label = 20, effect_label = 10, model_type = 25), 
  reverse_order = list(depvar_label = TRUE, effect_label = FALSE, model_type = FALSE), 
  order_vars = list(depvar_label = NULL, effect_label = NULL, model_type = NULL)
)

fig_data <- prep_reg_data(prep_reg_factors(ests, factor_params, include_valuelabel = FALSE), depvarlog = TRUE) %>% 
  mutate(depvar_label = "Predicted daily sales\nper worker (Current USD)")

 labels <- list(
      title = "Observational estimates of the effect of general digital technology adoption on labor productivity",
      subtitle = "", 
      y = NULL,
      x = NULL,
      caption = str_wrap(paste(SOURCE, fig_notes), CAP_WRAP*1.2)
    )

  barparams <- list(
  bars = list(width = 0.6, color = "grey90"), 
  valuelabels = list(show = FALSE, lab_vjust = 0, lab_hjust = 0, lab_ndgy = 0, lab_ndgx = 0.25, lab_face = "plain", lab_size = 3), 
  arrowlabels = list(show = TRUE, lab_vjust = 0.5, lab_hjust = 0.5, lab_ndgy = 0, lab_ndgx = -0.25,  lab_face = "plain", lab_size = 3),
  baselinelabel = list(show = TRUE, lab_vjust = 0, lab_hjust = 0.5, lab_ndgy = 0, lab_ndgx = 0,  lab_face = "bold", lab_size = 3.5)
) 


miny <- round(min(fig_data$fig_data), 2) 
maxy <- round(max(fig_data$fig_data), 2) 
buffer <- (maxy - miny)/100
miny <- miny - buffer*2
if (miny > 0) { miny <- 0 }
maxy <- maxy + buffer*2

scales <- list(
  y = list(limits = c(miny,maxy), position = "left", nbreaks = 3), 
  x = list(position = "bottom")
)

 facets <- list(type = "grid", rows ="depvar_label", cols = "model_type", scales = "free", space = "free", drop_row_label = FALSE) 
    
 fig_regests(fig_data, labels, facets = facets, barparams, scales, effect_desc = "The effect of an internet connection on labor productivity", coord_flip = FALSE)


```

---

```{r, fig.width = 12, fig.asp = 0.5}
#| label: fig-reg_revprhr_digtechusecase
#| echo: false
#| warning: false
#| fig-cap: "Relationship between digital technology adoption and firm-level labor productivity"
#| cap-location: margin

fig_notes <- "Notes: The results shown are based on a linear regression model that measures the effect of digital technology adoption on firm labor productivity. The 'unadjusted' model does not include any controls, while the 'adjusted' model includes controls for two variables: years of experience and educational attainment. An additional adjusted model controls for experience, education and psychological characteristics of the owner related to motivation, growth orientation and risk tolerance. The regression parameters are used to compute predicted probabilities to show the marginal effect of digital technology adoption on productivity. The height of 'Baseline' corresponds to the predicted productivity for firms run by an owner with mean years of experience, and secondary-level educaitonal attainment."
  
# Defining regressions
  depvars <- c("perf_revpdypemp_usd_log")
  depvar_labels <- INDICATORS[depvars]
  maineffects <- c("tech_function_comms", "tech_function_mkts_ops","tech_function_epay")
  effect_labels <- c("(Intercept)" = "No digital solutions used", INDICATORS[maineffects])
  confounds <- c("resp_experience_c", "resp_education_agg4_shc_non", "resp_education_agg4_shc_pri",  "resp_education_agg4_shc_trt")
  confounds2 <- c("resp_experience_c", "resp_education_agg4_shc_non", "resp_education_agg4_shc_pri",  "resp_education_agg4_shc_trt", "psych_mca_dim1", "psych_mca_dim2")
  
# Running regressions
ests <- bind_rows(
    map(depvars, model_and_prepfig, maineffects, confounds = NULL, data = main_data, depvar_labels, effect_labels, selected_country = COUNTRY, depvarlog = TRUE),
    map(depvars, model_and_prepfig, maineffects, confounds, data = main_data, depvar_labels, effect_labels, selected_country = COUNTRY, depvarlog = TRUE), 
    map(depvars, model_and_prepfig, maineffects, confounds2, data = main_data, depvar_labels, effect_labels, selected_country = COUNTRY, depvarlog = TRUE, model_type_override = "Model: Adjusted (+ pyschographics)") 
  ) %>% mutate(effect_label = str_replace(effect_label, ": Uses", ""))
    
factor_params <- list(
  wrap_sizes = list(depvar_label = 20, effect_label = 10, model_type = 25), 
  reverse_order = list(depvar_label = TRUE, effect_label = FALSE, model_type = FALSE), 
  order_vars = list(depvar_label = NULL, effect_label = NULL, model_type = NULL)
)

fig_data <- prep_reg_data(prep_reg_factors(ests, factor_params, include_valuelabel = FALSE), depvarlog = TRUE) %>% 
  mutate(depvar_label = "Predicted daily sales\nper worker (Current USD)")

 labels <- list(
      title = "Observational estimates of the effect of specific digital technologies on labor productivity",
      subtitle = "", 
      y = NULL,
      x = NULL,
      caption = str_wrap(paste(SOURCE, fig_notes), CAP_WRAP*1.2)
    )

  barparams <- list(
  bars = list(width = 0.6, color = "grey90"), 
  valuelabels = list(show = FALSE, lab_vjust = 0, lab_hjust = 0, lab_ndgy = 0, lab_ndgx = 0.25, lab_face = "plain", lab_size = 3), 
  arrowlabels = list(show = TRUE, lab_vjust = 0.5, lab_hjust = 0.5, lab_ndgy = 0, lab_ndgx = -0.25,  lab_face = "plain", lab_size = 3),
  baselinelabel = list(show = TRUE, lab_vjust = 0, lab_hjust = 0.5, lab_ndgy = 0, lab_ndgx = 0,  lab_face = "bold", lab_size = 3.5)
) 


miny <- round(min(fig_data$fig_data), 2) 
maxy <- round(max(fig_data$fig_data), 2) 
buffer <- (maxy - miny)/100
miny <- miny - buffer*2
if (miny > 0) { miny <- 0 }
maxy <- maxy + buffer*2

scales <- list(
  y = list(limits = c(miny,maxy), position = "left", nbreaks = 3), 
  x = list(position = "bottom")
)

 facets <- list(type = "grid", rows ="depvar_label", cols = "model_type", scales = "free", space = "free", drop_row_label = FALSE) 
    
 fig_regests(fig_data, labels, facets = facets, barparams, scales, effect_desc = "The effect of digital technology adoption on labor productivity", coord_flip = FALSE)


```


---

```{r, fig.width = 12, fig.asp = 0.45}
#| label: fig-reg_revprhr_digtechdepth
#| echo: false
#| warning: false
#| fig-cap: "Relationship between breadth of digital technology adoption and firm-level labor productivity"
#| cap-location: margin

fig_notes <- "Notes: The results shown are based on a linear regression model that measures the effect of digital technology adoption on firm labor productivity. The 'unadjusted' model does not include any controls, while the 'adjusted' model includes controls for two variables: years of experience and educational attainment. An additional adjusted model controls for experience, education and psychological characteristics of the owner related to motivation, growth orientation and risk tolerance. The regression parameters are used to compute predicted probabilities to show the marginal effect of digital technology adoption on productivity. The height of 'Baseline' corresponds to the predicted productivity for firms run by an owner with mean years of experience, and secondary-level educaitonal attainment."

# Defining regressions
  depvars <- c("perf_revpdypemp_usd_log")
  depvar_labels <- INDICATORS[depvars]
  maineffects <- c("tech_cat_any1", "tech_cat_any2", "tech_cat_any3all4")
  effect_labels <- c("(Intercept)" = "No digital solutions used", INDICATORS[maineffects])
   
  confounds <- c("resp_experience_c", "resp_education_agg4_shc_non", "resp_education_agg4_shc_pri",  "resp_education_agg4_shc_trt")
  confounds2 <- c("resp_experience_c", "resp_education_agg4_shc_non", "resp_education_agg4_shc_pri",  "resp_education_agg4_shc_trt", "psych_mca_dim1", "psych_mca_dim2")
  
# Running regressions
ests <- bind_rows(
    map(depvars, model_and_prepfig, maineffects, confounds = NULL, data = main_data, depvar_labels, effect_labels, selected_country = COUNTRY, depvarlog = TRUE),
    map(depvars, model_and_prepfig, maineffects, confounds, data = main_data, depvar_labels, effect_labels, selected_country = COUNTRY, depvarlog = TRUE), 
    map(depvars, model_and_prepfig, maineffects, confounds2, data = main_data, depvar_labels, effect_labels, selected_country = COUNTRY, depvarlog = TRUE, model_type_override = "Model: Adjusted (+ pyschographics)") 
  ) %>% mutate(effect_label = str_replace(effect_label, "Digital technology adoption:", ""))

factor_params <- list(
  wrap_sizes = list(depvar_label = 20, effect_label = 12, model_type = 25), 
  reverse_order = list(depvar_label = TRUE, effect_label = FALSE, model_type = FALSE), 
  order_vars = list(depvar_label = NULL, effect_label = NULL, model_type = NULL)
)

fig_data <- prep_reg_data(prep_reg_factors(ests, factor_params, include_valuelabel = FALSE), depvarlog = TRUE) %>% 
  mutate(depvar_label = "Predicted daily sales\nper worker (Current USD)")


 labels <- list(
      title = "Observational estimates of the effect of the breadth of digital technology adoption on labor productivity",
      subtitle = "",
      y = NULL,
      x = NULL,
      caption = str_wrap(paste(SOURCE, fig_notes), CAP_WRAP*1.2)
    )

barparams <- list(
  bars = list(width = 0.6, color = "grey90"), 
  valuelabels = list(show = FALSE, lab_vjust = 0, lab_hjust = 0, lab_ndgy = 0, lab_ndgx = 0.25, lab_face = "plain", lab_size = 3), 
  arrowlabels = list(show = TRUE, lab_vjust = 0.5, lab_hjust = 0.5, lab_ndgy = 0, lab_ndgx = -0.25,  lab_face = "plain", lab_size = 3), 
  baselinelabel = list(show = TRUE, lab_vjust = 0, lab_hjust = 0.5, lab_ndgy = 0, lab_ndgx = 0,  lab_face = "bold", lab_size = 3.5)
) 
  
 facets <- list(type = "grid", rows ="depvar_label", cols = "model_type", scales = "free", space = "free", drop_row_label = FALSE) 

  miny <- round(min(fig_data$fig_data), 2) 
  maxy <- round(max(fig_data$fig_data), 2) 
  buffer <- (maxy - miny)/100
  miny <- miny - buffer*4
  if (miny > 0) { miny <- 0 }
  maxy <- maxy + buffer*4

scales <- list(
  y = list(limits = c(miny,maxy), position = "left", nbreaks = 3), 
  x = list(position = "bottom")
)

 fig_regests(fig_data, labels, facets = facets, barparams, scales, effect_desc = "The effect of digital technology adoption on labor productivity", coord_flip = FALSE)
 
```




```{r, fig.width = 12, fig.asp = 0.5}
#| label: fig-reg_resilience_digitaladoption
#| echo: false
#| warning: false
#| fig-cap: "Relationship between digital technology and financial resilience"
#| cap-location: margin

fig_notes <- "Notes: The results shown are based on a linear regression model that measures the effect of digital technology adoption on the probability a firm can access emergency funds equivalent to 1 month of sales without major difficult. The 'unadjusted' model does not include any controls, while the 'adjusted' model includes controls for two variables: years of experience and educational attainment. An additional adjusted model controls for experience, education and psychological characteristics of the owner related to motivation, growth orientation and risk tolerance. The regression parameters are used to compute predicted probabilities to show the marginal effect of digital technology on financial resilience. The height of 'Baseline' corresponds to the predicted probability of financial resilience for firms run by an owner with mean years of experience, and secondary-level educaitonal attainment."
  
# Defining regressions
  depvars <- c("resi_capital_financial")
  depvar_labels <- INDICATORS[depvars]
  maineffects <- c("tech_uses_adoption_score_c")
  effect_labels <- c("(Intercept)" = "Baseline", INDICATORS[maineffects])
  confounds <- c("resp_experience_c", "resp_education_agg4_shc_non", "resp_education_agg4_shc_pri",  "resp_education_agg4_shc_trt")
  confounds2 <- c("resp_experience_c", "resp_education_agg4_shc_non", "resp_education_agg4_shc_pri",  "resp_education_agg4_shc_trt", "psych_mca_dim1", "psych_mca_dim2")
  
# Running regressions
ests <- bind_rows(
    map(depvars, model_and_prepfig, maineffects, confounds = NULL, data = main_data, depvar_labels, effect_labels, selected_country = COUNTRY, depvarlog = FALSE),
    map(depvars, model_and_prepfig, maineffects, confounds, data = main_data, depvar_labels, effect_labels, selected_country = COUNTRY, depvarlog = FALSE), 
    map(depvars, model_and_prepfig, maineffects, confounds2, data = main_data, depvar_labels, effect_labels, selected_country = COUNTRY, depvarlog = FALSE, model_type_override = "Model: Adjusted (+ pyschographics)") 
  )
    
factor_params <- list(
  wrap_sizes = list(depvar_label = 20, effect_label = 10, model_type = 25), 
  reverse_order = list(depvar_label = TRUE, effect_label = FALSE, model_type = FALSE), 
  order_vars = list(depvar_label = NULL, effect_label = NULL, model_type = NULL)
)

fig_data <- prep_reg_data(prep_reg_factors(ests, factor_params, include_valuelabel = FALSE), depvarlog = TRUE) %>% 
  mutate(depvar_label = "Predicted access to\nemergency funds (%)")

 labels <- list(
      title = "Observational estimates of the effect of general digital technology adoption on financial resilience",
      subtitle = "", 
      y = NULL,
      x = NULL,
      caption = str_wrap(paste(SOURCE, fig_notes), CAP_WRAP*1.2)
    )

  barparams <- list(
  bars = list(width = 0.6, color = "grey90"), 
  valuelabels = list(show = FALSE, lab_vjust = 0, lab_hjust = 0, lab_ndgy = 0, lab_ndgx = 0.25, lab_face = "plain", lab_size = 3), 
  arrowlabels = list(show = TRUE, lab_vjust = 0.5, lab_hjust = 0.5, lab_ndgy = 0, lab_ndgx = -0.25,  lab_face = "plain", lab_size = 3),
  baselinelabel = list(show = TRUE, lab_vjust = 0.5, lab_hjust = 0.5, lab_ndgy = 0.75, lab_ndgx = 0,  lab_face = "bold", lab_size = 3.5)
) 


miny <- round(min(fig_data$fig_data), 2) 
maxy <- round(max(fig_data$fig_data), 2) 
buffer <- (maxy - miny)/100
miny <- miny - buffer*2
if (miny > 0) { miny <- 0 }
maxy <- maxy + buffer*2

scales <- list(
  y = list(limits = c(miny,maxy), position = "left", nbreaks = 3), 
  x = list(position = "bottom")
)

 facets <- list(type = "grid", rows ="depvar_label", cols = "model_type", scales = "free", space = "free", drop_row_label = FALSE) 
    
 fig_regests(fig_data, labels, facets = facets, barparams, scales, effect_desc = "The effect (in percentage points) of digital technology on the probability of financial resilience", coord_flip = FALSE)


```

```{r, fig.width = 12, fig.asp = 0.5}
#| label: fig-reg_resilience_digtechusecase
#| echo: false
#| warning: false
#| fig-cap: "Relationship between digital technology adoption and financial resilience"
#| cap-location: margin

fig_notes <- "Notes: The results shown are based on a linear regression model that measures the effect of digital technology adoption on the probability a firm can access emergency funds equivalent to 1 month of sales without major difficult. The 'unadjusted' model does not include any controls, while the 'adjusted' model includes controls for two variables: years of experience and educational attainment. An additional adjusted model controls for experience, education and psychological characteristics of the owner related to motivation, growth orientation and risk tolerance. The regression parameters are used to compute predicted probabilities to show the marginal effect of digital technology on financial resilience. The height of 'Baseline' corresponds to the predicted probability of financial resilience for firms run by an owner with mean years of experience, and secondary-level educaitonal attainment."
  
# Defining regressions
  depvars <- c("resi_capital_financial")
  depvar_labels <- INDICATORS[depvars]
  maineffects <- c("tech_function_comms", "tech_function_mkts_ops","tech_function_epay")
  effect_labels <- c("(Intercept)" = "No digital solutions used", INDICATORS[maineffects])
  confounds <- c("resp_experience_c", "resp_education_agg4_shc_non", "resp_education_agg4_shc_pri",  "resp_education_agg4_shc_trt")
  confounds2 <- c("resp_experience_c", "resp_education_agg4_shc_non", "resp_education_agg4_shc_pri",  "resp_education_agg4_shc_trt", "psych_mca_dim1", "psych_mca_dim2")
  
# Running regressions
ests <- bind_rows(
    map(depvars, model_and_prepfig, maineffects, confounds = NULL, data = main_data, depvar_labels, effect_labels, selected_country = COUNTRY, depvarlog = FALSE),
    map(depvars, model_and_prepfig, maineffects, confounds, data = main_data, depvar_labels, effect_labels, selected_country = COUNTRY, depvarlog = FALSE), 
    map(depvars, model_and_prepfig, maineffects, confounds2, data = main_data, depvar_labels, effect_labels, selected_country = COUNTRY, depvarlog = FALSE, model_type_override = "Model: Adjusted (+ pyschographics)") 
  ) %>% mutate(effect_label = str_replace(effect_label, ": Uses", ""))
    
factor_params <- list(
  wrap_sizes = list(depvar_label = 20, effect_label = 10, model_type = 25), 
  reverse_order = list(depvar_label = TRUE, effect_label = FALSE, model_type = FALSE), 
  order_vars = list(depvar_label = NULL, effect_label = NULL, model_type = NULL)
)

fig_data <- prep_reg_data(prep_reg_factors(ests, factor_params, include_valuelabel = FALSE), depvarlog = TRUE) %>% 
  mutate(depvar_label = "Predicted access to\nemergency funds (%)")

 labels <- list(
      title = "Observational estimates of the effect of specific digital technologies on financial resilience",
      subtitle = "", 
      y = NULL,
      x = NULL,
      caption = str_wrap(paste(SOURCE, fig_notes), CAP_WRAP*1.2)
    )

  barparams <- list(
  bars = list(width = 0.6, color = "grey90"), 
  valuelabels = list(show = FALSE, lab_vjust = 0, lab_hjust = 0, lab_ndgy = 0, lab_ndgx = 0.25, lab_face = "plain", lab_size = 3), 
  arrowlabels = list(show = TRUE, lab_vjust = 0.5, lab_hjust = 0.5, lab_ndgy = 0, lab_ndgx = -0.25,  lab_face = "plain", lab_size = 3),
  baselinelabel = list(show = TRUE, lab_vjust = 0.5, lab_hjust = 0.5, lab_ndgy = 0.75, lab_ndgx = 0,  lab_face = "bold", lab_size = 3.5)
) 


miny <- round(min(fig_data$fig_data), 2) 
maxy <- round(max(fig_data$fig_data), 2) 
buffer <- (maxy - miny)/100
miny <- miny - buffer*2
if (miny > 0) { miny <- 0 }
maxy <- maxy + buffer*2

scales <- list(
  y = list(limits = c(miny,maxy), position = "left", nbreaks = 3), 
  x = list(position = "bottom")
)

 facets <- list(type = "grid", rows ="depvar_label", cols = "model_type", scales = "free", space = "free", drop_row_label = FALSE) 
    
 fig_regests(fig_data, labels, facets = facets, barparams, scales, effect_desc = "The effect (in percentage points) of digital technology on the probability of financial resilience", coord_flip = FALSE)


```


## Financial services 

```{r, fig.width = 12, fig.asp = 0.55}
#| label: fig-account_ownership
#| echo: false
#| warning: false
#| fig-cap: "Financical accounts and savings"
#| cap-location: margin

fig_notes <- c("Notes: Business savings account types are based on responses to the following question: Where are the business savings primarily kept? Common responses under other include: 'At home', 'Don't have savings' or saving with relatives, friends or neighbors. Savings account transaction channels are based on the following question: What are the options for transacting with this savings account? OTC represents 'Over the counter' and corresponds to the response option 'In-person through a physical branch location.")

if (COUNTRY == "Indonesia") {
  indicators <- c("fin_account_formal", "fin_account_formal_v2", "fin_account_formal_v3", "fin_account_formal_v4", "fin_owner_save", names(main_data)[str_detect(names(main_data), "bus_savings")])
} else { 
  indicators <- c("fin_account_formal", "fin_owner_save", names(main_data)[str_detect(names(main_data), "bus_savings")])
  }

groups <- GROUPS[c("fullsample", "business_size_agg2", "resp_sex_str")]

ests <- compute_summary_mainlevel_1g(indicators, groups, data = main_data, weights = "weight_msme_adj", psu = NULL, keep = "mean")

factor_params <- list(
  wrap_sizes = list(indicator_name = 60, indicator_group = 25, group_name = 25, group_cat_val = NULL), 
  reverse_order = list(indicator_name = TRUE, indicator_group = FALSE, group_name = FALSE, group_cat_val = FALSE), 
  order_vars = list(indicator_name = NULL, indicator_group = NULL, group_name = NULL, group_cat_val = NULL)
)

fig_data <- prep_fig_data(ests, factor_params)

labels <- list(
  title = "Account ownership and business savings",
  subtitle =  "MSEs (%)",
  yax_ti = NULL,
  xax_ti = NULL,
  caption = str_wrap(paste(SOURCE, fig_notes), CAP_WRAP)
)

figparams <- list(
  geom_type = "bar", # One of "bar" or "tile"
  bars = list(width = 0.8, position = "dodge", position_width = 0.9, labeltotal = FALSE, color = "white"), 
  valuelabels = list(show = FALSE, lab_hjust = 0, lab_face = "plain", lab_size = 3.5),
  catlabels = list(show = FALSE), 
  errorbars = list(show = FALSE, color = "#2374AB")
)

palette <- c("grey90", "#A2C3A4", "#C4F1BE", "#FF7B9C", "#CEE5F2")
names(palette) <- c("All businesses", "1 person", "2-10 people", "Women", "Men")   

scales <- list(
  fillcolor = list(palette = palette), 
  yaxis = list(limits = c(0, 1), nbreaks = 5, type = "percent", expand = NULL, droplines = TRUE)
)

legend <- list(
  show = TRUE, 
  title = NULL, 
  nrows = 1, 
  ncols = 1, 
  reverse = FALSE
)

vars <- list(
  xvar = "indicator_name", yvar = "mean", fillvar = "group_cat_val"
)

facets <- list(
  type = "grid", 
  rows = "indicator_group", 
  cols = "group_name", 
  scales = "free_y", 
  space = "free", 
  drop_row_label = FALSE, 
  drop_col_label = FALSE, 
  add_dividers = TRUE
)

fig_flex(fig_data, vars, facets, figparams, scales, legend, labels, coord_flip = TRUE) + theme(axis.text.x = element_text(size = 9))


```


---

```{r, fig.width = 12, fig.asp = 0.4}
#| label: fig-payments
#| echo: false
#| warning: false
#| fig-cap: "Merchant payments"
#| cap-location: margin

fig_notes <- c("Notes: The data in this question correspond to responses to the question 'In the last 12 months, what methods has the business used to accept payments from customers?'")

indicators <- c(names(main_data)[str_detect(names(main_data), "merchpay")])

groups <- GROUPS[c("fullsample", "business_size_agg2", "resp_sex_str")]

ests <- compute_summary_mainlevel_1g(indicators, groups, data = main_data, weights = "weight_msme_adj", psu = NULL, keep = "mean")

factor_params <- list(
  wrap_sizes = list(indicator_name = 50, indicator_group = 25, group_name = 25, group_cat_val = NULL), 
  reverse_order = list(indicator_name = TRUE, indicator_group = FALSE, group_name = FALSE, group_cat_val = FALSE), 
  order_vars = list(indicator_name = NULL, indicator_group = NULL, group_name = NULL, group_cat_val = NULL)
)

fig_data <- prep_fig_data(ests, factor_params)

labels <- list(
  title = "Merchant payments: Methods used by business to accept customer payments",
  subtitle =  "MSEs (%)",
  yax_ti = NULL,
  xax_ti = NULL,
  caption = str_wrap(paste(SOURCE, fig_notes), CAP_WRAP)
)

figparams <- list(
  geom_type = "bar", # One of "bar" or "tile"
  bars = list(width = 0.8, position = "dodge", position_width = 0.9, labeltotal = FALSE, color = "white"), 
  valuelabels = list(show = FALSE, lab_hjust = 0, lab_face = "plain", lab_size = 3.5),
  catlabels = list(show = FALSE), 
  errorbars = list(show = FALSE, color = "#2374AB")
)

palette <- c("grey90", "#A2C3A4", "#C4F1BE", "#FF7B9C", "#CEE5F2")
names(palette) <- c("All businesses", "1 person", "2-10 people", "Women", "Men")   

scales <- list(
  fillcolor = list(palette = palette), 
  yaxis = list(limits = c(0,1), nbreaks = 5, type = "percent", expand = NULL, droplines = TRUE)
)

legend <- list(
  show = TRUE, 
  title = NULL, 
  nrows = 1, 
  ncols = 1, 
  reverse = FALSE
)

vars <- list(
  xvar = "indicator_name", yvar = "mean", fillvar = "group_cat_val"
)

facets <- list(
  type = "grid", 
  rows = "indicator_group", 
  cols = "group_name", 
  scales = "free_y", 
  space = "free", 
  drop_row_label = TRUE, 
  drop_col_label = FALSE, 
  add_dividers = TRUE
)

fig_flex(fig_data, vars, facets, figparams, scales, legend, labels, coord_flip = TRUE)

```


---

```{r, fig.width = 12, fig.asp = 0.6}
#| label: fig-credit_demand
#| echo: false
#| warning: false
#| fig-cap: "Demand for credit"
#| cap-location: margin

fig_notes <- c("Notes: 'Used a loan or tried to obtain one in past 12 months' indicates whether the MSE had actively used a loan in the past 12 months OR tried to obtain a loan but coud not get one. The reasons for using credit are based on the following 'How did this business use the loans that were active in the last 12 months?', the reported percentages are for the subset of firms that had an active loan in the past 12 months")

indicators <- names(main_data)[str_detect(names(main_data), "activeloan_agg|activeloan_use")]
indicators <- indicators[!str_detect(indicators, "da")]
indicators <- c("fin_demandloan", "fin_activeloan_da_any", indicators) 

groups <- GROUPS[c("fullsample", "business_size_agg2", "resp_sex_str")]

ests <- compute_summary_mainlevel_1g(indicators, groups, data = main_data, weights = "weight_msme_adj", psu = NULL, keep = "mean")

factor_params <- list(
  wrap_sizes = list(indicator_name = 60, indicator_group = 35, group_name = 20, group_cat_val = NULL), 
  reverse_order = list(indicator_name = TRUE, indicator_group = FALSE, group_name = FALSE, group_cat_val = FALSE), 
  order_vars = list(indicator_name = NULL, indicator_group = NULL, group_name = NULL, group_cat_val = NULL)
)

fig_data <- prep_fig_data(ests, factor_params)

labels <- list(
  title = "Demand for credit and usage of loans (past 12 months)",
  subtitle =  "MSEs (%)",
  yax_ti = NULL,
  xax_ti = NULL,
  caption = str_wrap(paste(SOURCE, fig_notes), CAP_WRAP)
)

figparams <- list(
  geom_type = "bar", # One of "bar" or "tile"
  bars = list(width = 0.8, position = "dodge", position_width = 0.9, labeltotal = FALSE, color = "white"), 
  valuelabels = list(show = FALSE, lab_hjust = 0, lab_face = "plain", lab_size = 3.5),
  catlabels = list(show = FALSE), 
  errorbars = list(show = FALSE, color = "#2374AB")
)

palette <- c("grey90", "#A2C3A4", "#C4F1BE", "#FF7B9C", "#CEE5F2")
names(palette) <- c("All businesses", "1 person", "2-10 people", "Women", "Men")   

maxy <- roundupN(max(fig_data$mean, na.rm = TRUE))

scales <- list(
  fillcolor = list(palette = palette), 
  yaxis = list(limits = c(0, 1), nbreaks = 5, type = "percent", expand = NULL, droplines = TRUE)
)

legend <- list(
  show = TRUE, 
  title = NULL, 
  nrows = 1, 
  ncols = 1, 
  reverse = FALSE
)

vars <- list(
  xvar = "indicator_name", yvar = "mean", fillvar = "group_cat_val"
)

facets <- list(
  type = "grid", 
  rows = "indicator_group", 
  cols = "group_name", 
  scales = "free_y", 
  space = "free", 
  drop_row_label = FALSE, 
  drop_col_label = FALSE, 
  add_dividers = TRUE
)

fig_flex(fig_data, vars, facets, figparams, scales, legend, labels, coord_flip = TRUE)


```


---

```{r, fig.width = 12, fig.asp = 0.4}
#| label: fig-credit_denied
#| echo: false
#| warning: false
#| fig-cap: "Barriers to credit"
#| cap-location: margin

fig_notes <- "Notes: The reported percentages associated with 'Reason could not get loan' are among the subset of firms that were denied a loan in the past 12 months"

indicators <- c(names(main_data)[str_detect(names(main_data), "denied")])

groups <- GROUPS[c("fullsample", "business_size_agg2", "resp_sex_str")]

ests <- compute_summary_mainlevel_1g(indicators, groups, data = main_data, weights = "weight_msme_adj", psu = NULL, keep = "mean")

factor_params <- list(
  wrap_sizes = list(indicator_name = 60, indicator_group = 25, group_name = 20, group_cat_val = NULL), 
  reverse_order = list(indicator_name = TRUE, indicator_group = FALSE, group_name = FALSE, group_cat_val = FALSE), 
  order_vars = list(indicator_name = NULL, indicator_group = NULL, group_name = NULL, group_cat_val = NULL)
)

fig_data <- prep_fig_data(ests, factor_params)

labels <- list(
  title = "Barriers to credit",
  subtitle =  "MSEs (%)",
  yax_ti = NULL,
  xax_ti = NULL,
  caption = str_wrap(paste(SOURCE, fig_notes), CAP_WRAP)
)

figparams <- list(
  geom_type = "bar", # One of "bar" or "tile"
  bars = list(width = 0.8, position = "dodge", position_width = 0.9, labeltotal = FALSE, color = "white"), 
  valuelabels = list(show = FALSE, lab_hjust = 0, lab_face = "plain", lab_size = 3.5),
  catlabels = list(show = FALSE), 
  errorbars = list(show = FALSE, color = "#2374AB")
)

palette <- c("grey90", "#A2C3A4", "#C4F1BE", "#FF7B9C", "#CEE5F2")
names(palette) <- c("All businesses", "1 person", "2-10 people", "Women", "Men")   

maxy <- roundupN(max(fig_data$mean, na.rm = TRUE))

scales <- list(
  fillcolor = list(palette = palette), 
  yaxis = list(limits = c(0, maxy), nbreaks = 5, type = "percent", expand = NULL, droplines = TRUE)
)

legend <- list(
  show = TRUE, 
  title = NULL, 
  nrows = 1, 
  ncols = 1, 
  reverse = FALSE
)

vars <- list(
  xvar = "indicator_name", yvar = "mean", fillvar = "group_cat_val"
)

facets <- list(
  type = "grid", 
  rows = "indicator_group", 
  cols = "group_name", 
  scales = "free_y", 
  space = "free", 
  drop_row_label = FALSE, 
  drop_col_label = FALSE, 
  add_dividers = TRUE
)

fig_flex(fig_data, vars, facets, figparams, scales, legend, labels, coord_flip = TRUE)

```


---

```{r, fig.width = 12, fig.asp = 0.55}
#| label: fig-dfs_impacts
#| echo: false
#| warning: false
#| fig-cap: "Impacts of digital financial services"
#| cap-location: margin

fig_notes <- "Notes: This figure shows responses to two questions asked to users of digital financial services (including savings, loans, payments and insurance): (1) What effects has the use of financial services used through a phone, app, or computer on your business? (2) What are the main challenges the business has faced in using financial services used through a phone, app, or computer on your business?"
  
indicators <- c("fin_dfs_user", names(main_data)[str_detect(names(main_data), "digital_benefits|digital_challenges")])

groups <- GROUPS[c("fullsample", "business_size_agg2", "resp_sex_str")]

ests <- compute_summary_mainlevel_1g(indicators, groups, data = main_data, weights = "weight_msme_adj", psu = NULL, keep = "mean")

factor_params <- list(
  wrap_sizes = list(indicator_name = 60, indicator_group = 25, group_name = 20, group_cat_val = NULL), 
  reverse_order = list(indicator_name = TRUE, indicator_group = FALSE, group_name = FALSE, group_cat_val = FALSE), 
  order_vars = list(indicator_name = NULL, indicator_group = NULL, group_name = NULL, group_cat_val = NULL)
)

fig_data <- prep_fig_data(ests, factor_params)

labels <- list(
  title = "Benefits and challenges of digital financial services",
  subtitle =  "MSEs (%)",
  yax_ti = NULL,
  xax_ti = NULL,
  caption = str_wrap(paste(SOURCE, fig_notes), CAP_WRAP)
)

figparams <- list(
  geom_type = "bar", # One of "bar" or "tile"
  bars = list(width = 0.8, position = "dodge", position_width = 0.9, labeltotal = FALSE, color = "white"), 
  valuelabels = list(show = FALSE, lab_hjust = 0, lab_face = "plain", lab_size = 3.5),
  catlabels = list(show = FALSE), 
  errorbars = list(show = FALSE, color = "#2374AB")
)

palette <- c("grey90", "#A2C3A4", "#C4F1BE", "#FF7B9C", "#CEE5F2")
names(palette) <- c("All businesses", "1 person", "2-10 people", "Women", "Men")   

maxy <- roundupN(max(fig_data$mean, na.rm = TRUE))

scales <- list(
  fillcolor = list(palette = palette), 
  yaxis = list(limits = c(0, maxy), nbreaks = 5, type = "percent", expand = NULL, droplines = TRUE)
)

legend <- list(
  show = TRUE, 
  title = NULL, 
  nrows = 1, 
  ncols = 1, 
  reverse = FALSE
)

vars <- list(
  xvar = "indicator_name", yvar = "mean", fillvar = "group_cat_val"
)

facets <- list(
  type = "grid", 
  rows = "indicator_group", 
  cols = "group_name", 
  scales = "free_y", 
  space = "free", 
  drop_row_label = FALSE, 
  drop_col_label = FALSE, 
  add_dividers = TRUE
)

fig_flex(fig_data, vars, facets, figparams, scales, legend, labels, coord_flip = TRUE)

```


---

```{r, fig.width = 12, fig.asp = 0.5}
#| label: fig-ins
#| echo: false
#| warning: false
#| fig-cap: "Insurance usage"
#| cap-location: margin

fig_notes <- c("")

indicators <- c("fin_insur_lif_shc_cu" , "fin_insur_hlt_shc_cu", "fin_insur_acc_shc_cu", "fin_insur_bus_shc_cu", "fin_insur_aut_shc_cu", "fin_insur_any_shc_cu_comp")
groups <- GROUPS[c("fullsample", "resp_sex_str", "resp_education_agg4")]

ests <- compute_summary_mainlevel_1g(indicators, groups, data = main_data, weights = "weight_msme_adj", psu = NULL, keep = "mean")

factor_params <- list(
  wrap_sizes = list(indicator_name = 60, indicator_group = 25, group_name = 25, group_cat_val = NULL), 
  reverse_order = list(indicator_name = TRUE, indicator_group = FALSE, group_name = FALSE, group_cat_val = FALSE), 
  order_vars = list(indicator_name = NULL, indicator_group = NULL, group_name = NULL, group_cat_val = NULL)
)

fig_data <- prep_fig_data(ests, factor_params)

labels <- list(
  title = "Insurance coverage: Adoption",
  subtitle =  "MSE Owners or managers (%)",
  yax_ti = NULL,
  xax_ti = NULL,
  caption = str_wrap(paste(SOURCE, fig_notes), CAP_WRAP)
)

figparams <- list(
  geom_type = "bar", # One of "bar" or "tile"
  bars = list(width = 0.8, position = "dodge", position_width = 0.9, labeltotal = FALSE, color = "white"), 
  valuelabels = list(show = FALSE, lab_hjust = 0, lab_face = "plain", lab_size = 3.5),
  catlabels = list(show = FALSE), 
  errorbars = list(show = FALSE, color = "#2374AB")
)

palette <- c("grey90", "#FF7B9C", "#CEE5F2",  "#C4F1BE", "#A2C3A4", "#CEE5F2", "#2374AB")
names(palette) <- c("All businesses", "Women", "Men", "Some primary or none", "Completed primary or some secondary", "Completed secondary or some university/technical school", "Completed university/technical school")   

maxy <- roundupN(max(fig_data$mean, na.rm = TRUE))

scales <- list(
  fillcolor = list(palette = palette), 
  yaxis = list(limits = c(0, maxy), nbreaks = 5, type = "percent", expand = NULL, droplines = TRUE)
)

legend <- list(
  show = TRUE, 
  title = NULL, 
  nrows = 3, 
  ncols = 4, 
  reverse = FALSE
)

vars <- list(
  xvar = "indicator_group", yvar = "mean", fillvar = "group_cat_val"
)

facets <- list(
  type = "grid", 
  rows = "indicator_name", 
  cols = "group_name", 
  scales = "free_y", 
  space = "free", 
  drop_row_label = TRUE, 
  drop_col_label = FALSE, 
  add_dividers = TRUE
)

fig_flex(fig_data, vars, facets, figparams, scales, legend, labels, coord_flip = TRUE)

```

--- 

```{r, fig.width = 12, fig.asp = 0.5}
#| label: fig-reg_revprhr_finserv
#| echo: false
#| warning: false
#| fig-cap: "Relationship between financial services and firm-level labor productivity"
#| cap-location: margin

fig_notes <- "Notes: The results shown are based on a linear regression model that measures the effect of financial services on firm labor productivity. The 'unadjusted' model does not include any controls, while the 'adjusted' model includes controls for two variables: years of experience and educational attainment. An additional adjusted model controls for experience, education and psychological characteristics of the owner related to motivation, growth orientation and risk tolerance. The regression parameters are used to compute predicted probabilities to show the marginal effect of financial services on productivity. The height of 'Baseline' corresponds to the predicted productivity for firms run by an owner with mean years of experience, and secondary-level educaitonal attainment."
  
# Defining regressions
  depvars <- c("perf_revpdypemp_usd_log")
  depvar_labels <- INDICATORS[depvars]
  maineffects <- c("fin_account_formal", "fin_activeloan_agg_any", "fin_insur_any_shc_cu")
  effect_labels <- c("(Intercept)" = "No financial services used", INDICATORS[maineffects])
  confounds <- c("resp_experience_c", "resp_education_agg4_shc_non", "resp_education_agg4_shc_pri",  "resp_education_agg4_shc_trt")
  confounds2 <- c("resp_experience_c", "resp_education_agg4_shc_non", "resp_education_agg4_shc_pri",  "resp_education_agg4_shc_trt", "psych_mca_dim1", "psych_mca_dim2")
  
# Running regressions
ests <- bind_rows(
    map(depvars, model_and_prepfig, maineffects, confounds = NULL, data = main_data, depvar_labels, effect_labels, selected_country = COUNTRY, depvarlog = TRUE),
    map(depvars, model_and_prepfig, maineffects, confounds, data = main_data, depvar_labels, effect_labels, selected_country = COUNTRY, depvarlog = TRUE), 
    map(depvars, model_and_prepfig, maineffects, confounds2, data = main_data, depvar_labels, effect_labels, selected_country = COUNTRY, depvarlog = TRUE, model_type_override = "Model: Adjusted (+ pyschographics)") 
  ) %>% mutate(effect_label = str_replace(effect_label, ": Uses", ""))
    
factor_params <- list(
  wrap_sizes = list(depvar_label = 20, effect_label = 35, model_type = 25), 
  reverse_order = list(depvar_label = TRUE, effect_label = TRUE, model_type = FALSE), 
  order_vars = list(depvar_label = NULL, effect_label = NULL, model_type = NULL)
)

fig_data <- prep_reg_data(prep_reg_factors(ests, factor_params, include_valuelabel = FALSE), depvarlog = TRUE) %>% 
  mutate(depvar_label = "Predicted daily sales\nper worker (Current USD)")

 labels <- list(
      title = "Observational estimates of the effect of financial services on labor productivity",
      subtitle = "", 
      y = "Predicted daily sales per worker",
      x = NULL,
      caption = str_wrap(paste(SOURCE, fig_notes), CAP_WRAP*1.2)
    )

  barparams <- list(
  bars = list(width = 0.6, color = "grey90"), 
  valuelabels = list(show = FALSE, lab_vjust = 0, lab_hjust = 0, lab_ndgy = 0, lab_ndgx = 0.25, lab_face = "plain", lab_size = 3), 
  arrowlabels = list(show = TRUE, lab_vjust = 0.5, lab_hjust = 0.5, lab_ndgy = 0, lab_ndgx = -0.25,  lab_face = "plain", lab_size = 3),
  baselinelabel = list(show = TRUE, lab_vjust = 0.5, lab_hjust = 0, lab_ndgy = 0, lab_ndgx = 0,  lab_face = "bold", lab_size = 3.5)
) 


miny <- round(min(fig_data$fig_data), 2) 
maxy <- round(max(fig_data$fig_data), 2) 
buffer <- (maxy - miny)/100
miny <- miny - buffer*2
if (miny > 0) { miny <- 0 }
maxy <- maxy + buffer*2

scales <- list(
  y = list(limits = c(miny,maxy), position = "left", nbreaks = 3), 
  x = list(position = "bottom")
)

 facets <- list(type = "grid", rows ="depvar_label", cols = "model_type", scales = "free", space = "free", drop_row_label = TRUE) 
    
 fig_regests(fig_data, labels, facets = facets, barparams, scales, effect_desc = "The effect of financial services on labor productivity", coord_flip = TRUE)


```

```{r, fig.width = 12, fig.asp = 0.5}
#| label: fig-reg_resi_finserv
#| echo: false
#| warning: false
#| fig-cap: "Relationship between financial services and financial resilience"
#| cap-location: margin

fig_notes <- "Notes: The results shown are based on a linear regression model that measures the effect of financial services on the firm's ability to access emergency funds equivalent to 1 month of sales in 7 days. The 'unadjusted' model does not include any controls, while the 'adjusted' model includes controls for two variables: years of experience and educational attainment. An additional adjusted model controls for experience, education and psychological characteristics of the owner related to motivation, growth orientation and risk tolerance. The regression parameters are used to compute predicted probabilities to show the marginal effect of financial services on financial resilience. The height of 'Baseline' corresponds to the predicted probability of whether a firm can access emergency funds for firms run by an owner with mean years of experience, and secondary-level educaitonal attainment."
  
# Defining regressions
  depvars <- c("resi_capital_financial")
  depvar_labels <- INDICATORS[depvars]
  maineffects <- c("fin_account_formal", "fin_merchpay_noncash", "fin_activeloan_agg_any", "fin_insur_any_shc_cu")
  effect_labels <- c("(Intercept)" = "No financial services used", INDICATORS[maineffects])
  confounds <- c("resp_experience_c", "resp_education_agg4_shc_non", "resp_education_agg4_shc_pri",  "resp_education_agg4_shc_trt")
  confounds2 <- c("resp_experience_c", "resp_education_agg4_shc_non", "resp_education_agg4_shc_pri",  "resp_education_agg4_shc_trt", "psych_mca_dim1", "psych_mca_dim2")
  
# Running regressions
ests <- bind_rows(
    map(depvars, model_and_prepfig, maineffects, confounds = NULL, data = main_data, depvar_labels, effect_labels, selected_country = COUNTRY, depvarlog = FALSE),
    map(depvars, model_and_prepfig, maineffects, confounds, data = main_data, depvar_labels, effect_labels, selected_country = COUNTRY, depvarlog = FALSE), 
    map(depvars, model_and_prepfig, maineffects, confounds2, data = main_data, depvar_labels, effect_labels, selected_country = COUNTRY, depvarlog = FALSE, model_type_override = "Model: Adjusted (+ pyschographics)") 
  ) %>% mutate(effect_label = str_replace(effect_label, ": Uses", ""))
    
factor_params <- list(
  wrap_sizes = list(depvar_label = 20, effect_label = 35, model_type = 25), 
  reverse_order = list(depvar_label = TRUE, effect_label = TRUE, model_type = FALSE), 
  order_vars = list(depvar_label = NULL, effect_label = NULL, model_type = NULL)
)

fig_data <- prep_reg_data(prep_reg_factors(ests, factor_params, include_valuelabel = FALSE), depvarlog = FALSE) %>% 
  mutate(depvar_label = "Predicted probability of\n access to emergency funds (%)")

 labels <- list(
      title = "Observational estimates of the effect of financial services on financial resilience",
      subtitle = "", 
      y = "Predicted probability of access to emergency funds (%)",
      x = NULL,
      caption = str_wrap(paste(SOURCE, fig_notes), CAP_WRAP*1.2)
    )

  barparams <- list(
  bars = list(width = 0.6, color = "grey90"), 
  valuelabels = list(show = FALSE, lab_vjust = 0, lab_hjust = 0, lab_ndgy = 0, lab_ndgx = 0.25, lab_face = "plain", lab_size = 3), 
  arrowlabels = list(show = TRUE, lab_vjust = 0.5, lab_hjust = 0.5, lab_ndgy = 0, lab_ndgx = -0.25,  lab_face = "plain", lab_size = 3),
  baselinelabel = list(show = TRUE, lab_vjust = 0.5, lab_hjust = 0, lab_ndgy = 0, lab_ndgx = 0,  lab_face = "bold", lab_size = 3.5)
) 


miny <- round(min(fig_data$fig_data), 2) 
maxy <- round(max(fig_data$fig_data), 2) 
buffer <- (maxy - miny)/100
miny <- miny - buffer*2
if (miny > 0) { miny <- 0 }
maxy <- maxy + buffer*2

scales <- list(
  y = list(limits = c(miny,maxy), position = "left", nbreaks = 3), 
  x = list(position = "bottom")
)

 facets <- list(type = "grid", rows ="depvar_label", cols = "model_type", scales = "free", space = "free", drop_row_label = TRUE) 
    
 fig_regests(fig_data, labels, facets = facets, barparams, scales, effect_desc = "The effect of financial services on the probability a firm can access emergency funds", coord_flip = TRUE)


```

## Consumer protection

```{r, fig.width = 12, fig.asp = 0.5}
#| label: fig-cp_loanrepayment
#| echo: false
#| warning: false
#| fig-cap: "Challenges with loan repayment"
#| cap-location: margin

fig_notes <- "Notes: The two questions on loan repayment difficulty were only asked to MSEs that had an active loan in the past 12 months, the questions are: (1) In the last 12 months, has the business been unable to pay a full loan installment on-time for any funds that it borrowed? and (2) How did you cope with this difficulty to repay?"
  
indicators <- c(names(main_data)[str_detect(names(main_data), "loanrepaydiff")])

groups <- GROUPS[c("fullsample", "business_size_agg2", "resp_sex_str")]

ests <- compute_summary_mainlevel_1g(indicators, groups, data = main_data, weights = "weight_msme_adj", psu = NULL, keep = "mean")  %>% 
  mutate(indicator_group = ifelse(str_detect(indicator, "cope"), "Coping strategy", indicator_group))

factor_params <- list(
  wrap_sizes = list(indicator_name = 60, indicator_group = 25, group_name = 20, group_cat_val = NULL), 
  reverse_order = list(indicator_name = TRUE, indicator_group = FALSE, group_name = FALSE, group_cat_val = FALSE), 
  order_vars = list(indicator_name = NULL, indicator_group = NULL, group_name = NULL, group_cat_val = NULL)
)

fig_data <- prep_fig_data(ests, factor_params) 

labels <- list(
  title = "Challenges with loan repayment",
  subtitle =  "MSEs with active loans in the past 12 months (%)",
  yax_ti = NULL,
  xax_ti = NULL,
  caption = str_wrap(paste(SOURCE, fig_notes), CAP_WRAP)
)

figparams <- list(
  geom_type = "bar", # One of "bar" or "tile"
  bars = list(width = 0.8, position = "dodge", position_width = 0.9, labeltotal = FALSE, color = "white"), 
  valuelabels = list(show = FALSE, lab_hjust = 0, lab_face = "plain", lab_size = 3.5),
  catlabels = list(show = FALSE), 
  errorbars = list(show = FALSE, color = "#2374AB")
)

palette <- c("grey70", "#A2C3A4", "#C4F1BE", "#FF7B9C", "#CEE5F2")
names(palette) <- c("All businesses", "1 person", "2-10 people", "Women", "Men")   

maxy <- roundupN(max(fig_data$mean, na.rm = TRUE))

scales <- list(
  fillcolor = list(palette = palette), 
  yaxis = list(limits = c(0, maxy), nbreaks = 5, type = "percent", expand = NULL, droplines = TRUE)
)

legend <- list(
  show = TRUE, 
  title = NULL, 
  nrows = 1, 
  ncols = 1, 
  reverse = FALSE
)

vars <- list(
  xvar = "indicator_name", yvar = "mean", fillvar = "group_cat_val"
)

facets <- list(
  type = "grid", 
  rows = "indicator_group", 
  cols = "group_name", 
  scales = "free_y", 
  space = "free", 
  drop_row_label = FALSE, 
  drop_col_label = FALSE, 
  add_dividers = TRUE
)

fig_flex(fig_data, vars, facets, figparams, scales, legend, labels, coord_flip = TRUE)

```


---

```{r, fig.width = 12, fig.asp = 0.6}
#| label: fig-cp_issues
#| echo: false
#| warning: false
#| fig-cap: "Consumer protection issues"
#| cap-location: margin

fig_notes <- "Notes: This figure shows responses to five questions relating to consumer risks, disputes and redress: (1) In the last 12 months, have you encountered any of the following issues with financial services?, (2) When you encountered an issue with digital financial services, did you raise an official complaint?, (3) Why didn't you raise a complaint?, (4) If you raised an official complaint, was the issue resolved? and (5) Have you ever stopped using any digital financial services due to fear of, or experiencing, the risks discussed above?"

indicators <- c(names(main_data)[str_detect(names(main_data), "cp_issues|cp_complaint|cp_dfs_stopped")])

groups <- GROUPS[c("fullsample", "resp_sex_str")]

# Adjustment for India
if (COUNTRY == "India") { 
  main_data <- main_data %>% mutate(cp_complaint_resolved_yes = ifelse(resp_sex_str == "Women", 0, cp_complaint_resolved_yes))
}

ests <- compute_summary_mainlevel_1g(indicators, groups, data = main_data, weights = "weight_msme_adj", psu = NULL, keep = "mean") %>% 
  mutate(indicator_group = ifelse(str_detect(indicator, "cope"), "Coping strategy", indicator_group))

factor_params <- list(
  wrap_sizes = list(indicator_name = 60, indicator_group = 35, group_name = 25, group_cat_val = NULL), 
  reverse_order = list(indicator_name = TRUE, indicator_group = FALSE, group_name = FALSE, group_cat_val = FALSE), 
  order_vars = list(indicator_name = NULL, indicator_group = NULL, group_name = NULL, group_cat_val = NULL)
)

fig_data <- prep_fig_data(ests, factor_params) 

labels <- list(
  title = "Consumer protection issues",
  subtitle =  "MSEs (%)",
  yax_ti = NULL,
  xax_ti = NULL,
  caption = str_wrap(paste(SOURCE, fig_notes), CAP_WRAP)
)

figparams <- list(
  geom_type = "bar", # One of "bar" or "tile"
  bars = list(width = 0.8, position = "dodge", position_width = 0.9, labeltotal = FALSE, color = "white"), 
  valuelabels = list(show = FALSE, lab_hjust = 0, lab_face = "plain", lab_size = 3.5),
  catlabels = list(show = FALSE), 
  errorbars = list(show = FALSE, color = "#2374AB")
)

palette <- c("grey70", "#A2C3A4", "#C4F1BE", "#FF7B9C", "#CEE5F2")
names(palette) <- c("All businesses", "1 person", "2-10 people", "Women", "Men")   

maxy <- roundupN(max(fig_data$mean, na.rm = TRUE))

scales <- list(
  fillcolor = list(palette = palette), 
  yaxis = list(limits = c(0, maxy), nbreaks = 5, type = "percent", expand = NULL, droplines = TRUE)
)

legend <- list(
  show = TRUE, 
  title = NULL, 
  nrows = 1, 
  ncols = 1, 
  reverse = FALSE
)

vars <- list(
  xvar = "indicator_name", yvar = "mean", fillvar = "group_cat_val"
)

facets <- list(
  type = "grid", 
  rows = "indicator_group", 
  cols = "group_name", 
  scales = "free_y", 
  space = "free", 
  drop_row_label = FALSE, 
  drop_col_label = FALSE, 
  add_dividers = TRUE
)

fig_flex(fig_data, vars, facets, figparams, scales, legend, labels, coord_flip = TRUE)

```



## Risks and Resilience

```{r, fig.width = 12, fig.asp = 0.4}
#| label: fig-risks_types
#| echo: false
#| warning: false
#| fig-cap: "Risks: General"
#| cap-location: margin

indicators <- c("risk_largestimpact_shc_corr", "risk_largestimpact_shc_cost", "risk_largestimpact_shc_crme", "risk_largestimpact_shc_frau", "risk_largestimpact_shc_hlth", "risk_largestimpact_shc_none", "risk_largestimpact_shc_othr", "risk_largestimpact_shc_wthr")

groups <- GROUPS[c("fullsample", "business_size_agg2", "resp_sex_str")]

ests <- compute_summary_mainlevel_1g(indicators, groups, data = main_data, weights = "weight_msme_adj", psu = NULL, keep = "mean")

factor_params <- list(
  wrap_sizes = list(indicator_name = 40, indicator_group = 25, group_name = 25, group_cat_val = NULL), 
  reverse_order = list(indicator_name = TRUE, indicator_group = FALSE, group_name = FALSE, group_cat_val = FALSE), 
  order_vars = list(indicator_name = NULL, indicator_group = NULL, group_name = NULL, group_cat_val = NULL)
)

fig_data <- prep_fig_data(ests %>% filter(indicator_name != "No risks faced"), factor_params)

labels <- list(
  title = "High impact shocks faced by MSEs",
  subtitle =  str_wrap("In the last 36 months (3 years), which of the following risks had the largest impact (most costly) in terms of losses or expenses incurred by the business?", 120), 
  yax_ti = NULL,
  xax_ti = NULL,
  caption = SOURCE
)

figparams <- list(
  geom_type = "bar", # One of "bar" or "tile"
  bars = list(width = 0.8, position = "dodge", position_width = 0.9, labeltotal = FALSE, color = "white"), 
  valuelabels = list(show = FALSE, lab_hjust = 0, lab_face = "plain", lab_size = 3.5),
  catlabels = list(show = FALSE), 
  errorbars = list(show = FALSE, color = "#2374AB")
)

palette <- c("grey70", "#A2C3A4", "#C4F1BE", "#FF7B9C", "#CEE5F2")
names(palette) <- c("All businesses", "1 person", "2-10 people", "Women", "Men")   

maxy <- roundupN(max(fig_data$mean, na.rm = TRUE))

scales <- list(
  fillcolor = list(palette = palette), 
  yaxis = list(limits = c(0, maxy), nbreaks = 5, type = "percent", expand = NULL, droplines = TRUE)
)

legend <- list(
  show = TRUE, 
  title = NULL, 
  nrows = 1, 
  ncols = 1, 
  reverse = FALSE
)

vars <- list(
  xvar = "indicator_name", yvar = "mean", fillvar = "group_cat_val"
)

facets <- list(
  type = "grid", 
  rows = "indicator_group", 
  cols = "group_name", 
  scales = "free_y", 
  space = "free",
  drop_row_label = TRUE, 
  drop_col_label = FALSE, 
  add_dividers = FALSE
)

fig_flex(fig_data, vars, facets, figparams, scales, legend, labels, coord_flip = TRUE)


```


---

```{r, fig.width = 12, fig.asp = 0.35}
#| label: fig-risks_climate_types
#| echo: false
#| warning: false
#| fig-cap: "Risks: Climate"
#| cap-location: margin

indicators <- c("risk_weather_type_heat", "risk_weather_type_droughts", "risk_weather_type_floodstyphoon", "risk_weather_type_other", "risk_weather_type_any")
groups <- GROUPS[c("fullsample", "business_size_agg2", "resp_sex_str")]

ests <- compute_summary_mainlevel_1g(indicators, groups, data = main_data, weights = "weight_msme_adj", psu = NULL, keep = "mean")

factor_params <- list(
  wrap_sizes = list(indicator_name = 40, indicator_group = 25, group_name = 25, group_cat_val = NULL), 
  reverse_order = list(indicator_name = TRUE, indicator_group = FALSE, group_name = FALSE, group_cat_val = FALSE), 
  order_vars = list(indicator_name = NULL, indicator_group = NULL, group_name = NULL, group_cat_val = NULL)
)

fig_data <- prep_fig_data(ests, factor_params)

labels <- list(
  title = "Climate shocks faced by MSEs",
  subtitle =  str_wrap("In the last 36 months (3 years), has your business or the supply chain of your business experienced any of the following weather-related risks?", 120), 
  yax_ti = NULL,
  xax_ti = NULL,
  caption = str_wrap(paste(SOURCE, "Notes: *For Indonesia and India, extreme rain, floods or landslides includes typhoons or cyclones"), CAP_WRAP)
)

figparams <- list(
  geom_type = "bar", # One of "bar" or "tile"
  bars = list(width = 0.8, position = "dodge", position_width = 0.9, labeltotal = FALSE, color = "white"), 
  valuelabels = list(show = FALSE, lab_hjust = 0, lab_face = "plain", lab_size = 3.5),
  catlabels = list(show = FALSE), 
  errorbars = list(show = FALSE, color = "#2374AB")
)

palette <- c("grey70", "#A2C3A4", "#C4F1BE", "#FF7B9C", "#CEE5F2")
names(palette) <- c("All businesses", "1 person", "2-10 people", "Women", "Men")   

maxy <- roundupN(max(fig_data$mean, na.rm = TRUE))

scales <- list(
  fillcolor = list(palette = palette, direction = NULL), 
  yaxis = list(limits = c(0, maxy), nbreaks = 5, type = "percent", expand = NULL, droplines = TRUE)
)

legend <- list(
  show = TRUE, 
  title = NULL, 
  nrows = 1, 
  ncols = 1, 
  reverse = FALSE
)

vars <- list(
  xvar = "indicator_name", yvar = "mean", fillvar = "group_cat_val"
)

facets <- list(
  type = "grid", 
  rows = "indicator_group", 
  cols = "group_name", 
  scales = "free_y", 
  space = "free",
  drop_row_label = TRUE, 
  drop_col_label = FALSE, 
  add_dividers = FALSE
)

fig_flex(fig_data, vars, facets, figparams, scales, legend, labels, coord_flip = TRUE)


```

---

```{r, fig.width = 12, fig.asp = 0.5}
#| label: fig-risks_impacts
#| echo: false
#| warning: false
#| fig-cap: "Risks: Impacts"
#| cap-location: margin

fig_notes <- c("Notes: This figure shows responses to three questions related to the impact of weather shocks: (1) Please think about the weather risk that affected you the most in the last 36 months and describe how the weather risk impacted your business operations, (2) What actions did the business take to cope with the impacts of this weather risk? abd (3) What is the condition of the business now, compared to before the weather risk occurred?")

indicators <- c(names(main_data)[str_detect(names(main_data), "weather_impact")], names(main_data)[str_detect(names(main_data), "weather_cope")], names(main_data)[str_detect(names(main_data), "weather_cond")])

groups <- GROUPS[c("fullsample", "business_size_agg2", "business_sector_agg2")]

ests <- compute_summary_mainlevel_1g(indicators, groups, data = main_data, weights = "weight_msme_adj", psu = NULL, keep = "mean")

factor_params <- list(
  wrap_sizes = list(indicator_name = 60, indicator_group = 25, group_name = 25, group_cat_val = NULL), 
  reverse_order = list(indicator_name = TRUE, indicator_group = FALSE, group_name = FALSE, group_cat_val = FALSE), 
  order_vars = list(indicator_name = NULL, indicator_group = NULL, group_name = NULL, group_cat_val = NULL)
)

fig_data <- prep_fig_data(ests, factor_params)

labels <- list(
  title = "Climate shocks: Impacts and coping strategies",
  subtitle =  "MSEs exposed to a climate shock in past 36 months (%)",
  yax_ti = NULL,
  xax_ti = NULL,
  caption = str_wrap(paste(SOURCE, fig_notes), CAP_WRAP)
)

figparams <- list(
  geom_type = "tile", # One of "bar" or "tile"
  tiles = list(color = "white"), 
  valuelabels = list(show = TRUE, lab_hjust = 0.5, lab_face = "plain", lab_size = 3),
  catlabels = list(show = FALSE), 
  errorbars = list(show = FALSE, color = "#2374AB")
)

scales <- list(
  fillcolor = list(palette = "Blues", direction = 1), 
  yaxis = list(limits = c(0, 1), nbreaks = 5, type = "percent", expand = NULL, droplines = TRUE)
)

legend <- list(
  show = FALSE, 
  title = NULL, 
  nrows = 1, 
  ncols = 1, 
  reverse = FALSE
)

vars <- list(
  xvar = "indicator_name", yvar = "group_cat_val", fillvar = "mean"
)

facets <- list(
  type = "grid", 
  rows = "indicator_group", 
  cols = "group_name", 
  scales = "free", 
  space = "free",
  drop_row_label = FALSE, 
  drop_col_label = FALSE, 
  add_dividers = FALSE
)

fig_flex(fig_data, vars, facets, figparams, scales, legend, labels, coord_flip = TRUE)


```


---

```{r, fig.width = 12, fig.asp = 0.45}
#| label: fig-resilience_financial
#| echo: false
#| warning: false
#| fig-cap: "Financial resilience"
#| cap-location: margin

fig_notes <- c("Notes: This figure is based on responses to two questions: (1) Imagine that your business had an emergency and needed to pay money equivalent to 1 month of business revenue, how difficult would it be for you to come up with that amount in the next 7 days? and (2) What would be the MAIN source of money that the business would use to come up with this lump sum amount? The percentages in the right panel correspond to the % of MSEs reporting that raising emergency funds is possible.")

indicators <- c("resi_efunds_firm_diff_1",   "resi_efunds_firm_diff_2", "resi_efunds_firm_diff_3", "resi_efunds_firm_diff_4", 
  "resi_efunds_firm_source_family", "resi_efunds_firm_source_work", "resi_efunds_firm_source_firmcsh", "resi_efunds_firm_source_hhcsh", "resi_efunds_firm_source_borrow", "resi_efunds_firm_source_sellassets", "resi_efunds_firm_source_other")

groups <- GROUPS[c("fullsample", "business_size_agg2", "business_sector_agg2", "resp_sex_str")]

ests <- compute_summary_mainlevel_1g(indicators, groups, data = main_data, weights = "weight_msme_adj", psu = NULL, keep = "mean")

factor_params <- list(
  wrap_sizes = list(indicator_name = 60, indicator_group = 25, group_name = 25, group_cat_val = NULL), 
  reverse_order = list(indicator_name = TRUE, indicator_group = FALSE, group_name = FALSE, group_cat_val = FALSE), 
  order_vars = list(indicator_name = NULL, indicator_group = NULL, group_name = NULL, group_cat_val = NULL)
)

fig_data <- prep_fig_data(ests, factor_params)


labels <- list(
  title = NULL, 
  subtitle =  NULL, 
  yax_ti = NULL,
  xax_ti = NULL,
  caption = NULL
)

figparams <- list(
  geom_type = "bar", # One of "bar" or "tile"
  bars = list(width = 0.9, position = "stack", labeltotal = FALSE, color = "white"), 
  valuelabels = list(show = FALSE, lab_hjust = 0.5, lab_vjust = 0.5, lab_face = "plain", lab_size = 3),
  catlabels = list(show = FALSE), 
  errorbars = list(show = FALSE)
)

palette <- c("#A2C3A4", "#C4F1BE", "#FF9F1C", "#DB504A", "#31AFD4", "#CEE5F2", "#CE6A85", "#985277", "#FAA275", "#FF8C61", "grey80")
names(palette) <- unique(fig_data$indicator_name)

scales <- list(
  fillcolor = list(palette = palette, direction = NULL), 
  yaxis = list(limits = c(0, 1), nbreaks = 5, type = "percent", expand = NULL, droplines = FALSE)
)

legend <- list(
  show = TRUE, 
  title = NULL, 
  direction = "horizontal",
  nrows = 2, 
  ncols = 1, 
  reverse = TRUE
)

vars <- list(
  xvar = "group_cat_val", yvar = "mean", fillvar = "indicator_name"
)

facets <- list(
  type = "grid", 
  rows = "group_name", 
  cols = "indicator_group", 
  scales = "free", 
  space = "free",
  drop_row_label = FALSE, 
  drop_col_label = FALSE, 
  add_dividers = FALSE
)

p1 <- fig_flex(fig_data %>% filter(indicator %in% names(main_data)[str_detect(names(main_data), "efunds_firm_diff")]),
                     vars, facets, figparams, scales, legend, labels, coord_flip = TRUE) 

facets <- list(
  type = "grid", 
  rows = "group_name", 
  cols = "indicator_group", 
  scales = "free", 
  space = "free",
  drop_row_label = TRUE, 
  drop_col_label = FALSE, 
  add_dividers = FALSE
)

p2 <- fig_flex(fig_data %>% filter(indicator %in% names(main_data)[str_detect(names(main_data), "efunds_firm_source")]),
                     vars, facets, figparams, scales, legend, labels, coord_flip = TRUE)  

p1 + p2 + plot_layout(axes = "collect") + 
  plot_annotation(title = "Financial resilience: Access to- and source of- emergency funds", 
                  subtitle = "MSEs (%)", 
                  caption = str_wrap(paste(SOURCE, fig_notes), CAP_WRAP), 
                  theme = theme(plot.title = element_text(size = 14, hjust = 0, face = 'bold', color = 'black'), 
                                      plot.caption=element_text(hjust=0, color="gray30", size=12),
                                      plot.title.position = "plot",
                                      plot.caption.position = "plot")) 

```


---

```{r, fig.width = 12, fig.asp = 0.5}
#| label: fig-resilience_nonfinancial
#| echo: false
#| warning: false
#| fig-cap: "Other dimensions of business resilience"
#| cap-location: margin

fig_notes <- "Notes: This figure is based on responses to three questions (1) (To owners only) If your household has an emergency that requires  [1/20 of GNI per capita] in cash within the next 7 days, would you need to take resources from the business to cover this emergency, (2) If your main customer were to permanently stop purchasing from your business, or if your main suplier were to close operations, how difficult would this be for your business? and (3) If you needed support to sustain your business operations, how confident are you in relying on your network?"

indicators <- c(names(main_data)[str_detect(names(main_data), "efunds_hh_owner")],
                names(main_data)[str_detect(names(main_data), "suppchain_cust")], 
                names(main_data)[str_detect(names(main_data), "network_conf")])
indicators <- indicators[!str_detect(indicators, "score")]

groups <- GROUPS[c("fullsample", "business_size_agg2", "business_sector_agg2", "resp_sex_str")]

ests <- compute_summary_mainlevel_1g(indicators, groups, data = main_data, weights = "weight_msme_adj", psu = NULL, keep = "mean")

factor_params <- list(
  wrap_sizes = list(indicator_name = 60, indicator_group = 25, group_name = 25, group_cat_val = NULL), 
  reverse_order = list(indicator_name = TRUE, indicator_group = FALSE, group_name = FALSE, group_cat_val = FALSE), 
  order_vars = list(indicator_name = NULL, indicator_group = NULL, group_name = NULL, group_cat_val = NULL)
)

fig_data <- prep_fig_data(ests, factor_params)

fct_levels <- c("No", "Yes", "Not difficult at all",  "Somewhat difficult", "Very difficult", "Very confident", "Somewhat confident", "Not confident")

fig_data <- fig_data %>% mutate(indicator_name = fct_rev(factor(indicator_name, levels = fct_levels, ordered = TRUE)))

labels <- list(
  title = NULL, 
  subtitle =  NULL, 
  yax_ti = NULL,
  xax_ti = NULL,
  caption = NULL
)

figparams <- list(
  geom_type = "bar", # One of "bar" or "tile"
  bars = list(width = 0.9, position = "stack", labeltotal = FALSE, color = "white"), 
  valuelabels = list(show = FALSE, lab_hjust = 0.5, lab_vjust = 0.5, lab_face = "plain", lab_size = 3),
  catlabels = list(show = FALSE), 
  errorbars = list(show = FALSE)
)

palette <- c("#DB504A", "#31AFD4", "#A2C3A4", "#FF9F1C", "#DB504A", "#DB504A", "#FF9F1C", "#A2C3A4")
names(palette) <- unique(fig_data$indicator_name)

scales <- list(
  fillcolor = list(palette = palette, direction = NULL), 
  yaxis = list(limits = c(0, 1), nbreaks = 5, type = "percent", expand = NULL, droplines = FALSE)
)

legend <- list(
  show = TRUE, 
  title = NULL, 
  direction = "horizontal",
  nrows = 3, 
  ncols = 1, 
  reverse = TRUE
)

vars <- list(
  xvar = "group_cat_val", yvar = "mean", fillvar = "indicator_name"
)

facets <- list(
  type = "grid", 
  rows = "group_name", 
  cols = "indicator_group", 
  scales = "free", 
  space = "free",
  drop_row_label = FALSE, 
  drop_col_label = FALSE, 
  add_dividers = FALSE
)


p1 <- fig_flex(fig_data %>% filter(indicator %in% names(main_data)[str_detect(names(main_data), "resi_efunds_hh_owner")]),
                     vars, facets, figparams, scales, legend, labels, coord_flip = TRUE) 


facets <- list(
  type = "grid", 
  rows = "group_name", 
  cols = "indicator_group", 
  scales = "free", 
  space = "free",
  drop_row_label = TRUE, 
  drop_col_label = FALSE, 
  add_dividers = FALSE
)


p2 <- fig_flex(fig_data %>% filter(indicator %in% names(main_data)[str_detect(names(main_data), "suppchain_cust")]), 
               vars, facets, figparams, scales, legend, labels, coord_flip = TRUE) 

p3 <- fig_flex(fig_data %>% filter(indicator %in% names(main_data)[str_detect(names(main_data), "network_conf")]), 
                     vars, facets, figparams, scales, legend, labels, coord_flip = TRUE) 


p1 + p2 + p3 + plot_layout(axes = "collect") + 
  plot_annotation(title = "Other dimensions of business resilience", 
                  subtitle = "MSEs (%)", 
                  caption = str_wrap(paste(SOURCE, fig_notes), CAP_WRAP), 
                  theme = theme(plot.title = element_text(size = 14, hjust = 0, face = 'bold', color = 'black'), 
                                      plot.caption=element_text(hjust=0, color="gray30", size=12),
                                      plot.title.position = "plot",
                                      plot.caption.position = "plot")) 

```


---

```{r, fig.width = 12, fig.asp = 0.4}
#| label: fig-resilience_overview
#| echo: false
#| warning: false
#| fig-cap: "Resilience capital"
#| cap-location: margin

fig_notes <- "Notes: The overall resilience score is a composite variable that considers the the degree of difficulty of raising emergency funds, the degree of difficulty of losing a main customer or supplier and the degree of confidence in the owner's social networks an resilience capital and whether the business finances are insulated from household shocks. The score is normalized so that a score of 0 denotes the lowest potential resilience and a score of 1 denotes the highest potential resilience."

indicators <- c(names(main_data)[str_detect(names(main_data), "resi_capital")])
indicators <- indicators[!str_detect(indicators, "resi_capital_score_v1|resi_capital_score_v2|resi_capital_score_v3")]
indicators <- c(indicators, "resi_capital_score_v3_norm")

groups <- GROUPS[c("fullsample", "business_size_agg2", "business_sector_agg2", "resp_sex_str")]

ests <- compute_summary_mainlevel_1g(indicators, groups, data = main_data, weights = "weight_msme_adj", psu = NULL, keep = "mean")

factor_params <- list(
  wrap_sizes = list(indicator_name = 60, indicator_group = 25, group_name = 25, group_cat_val = NULL), 
  reverse_order = list(indicator_name = TRUE, indicator_group = FALSE, group_name = FALSE, group_cat_val = FALSE), 
  order_vars = list(indicator_name = NULL, indicator_group = NULL, group_name = NULL, group_cat_val = NULL)
)

fig_data <- prep_fig_data(ests, factor_params)
fig_data <- resilience_capital(fig_data) %>% mutate(indicator_group2 = fct_inorder(indicator_group2))

labels <- list(
  title = "Resilience capital",
  subtitle =  "MSEs (%)",
  yax_ti = NULL,
  xax_ti = NULL,
  caption = str_wrap(paste(SOURCE, fig_notes), CAP_WRAP)
)

figparams <- list(
  geom_type = "tile", # One of "bar" or "tile"
  tiles = list(color = "white"), 
  valuelabels = list(show = TRUE, lab_hjust = 0.5, lab_face = "plain", lab_size = 3.5),
  catlabels = list(show = FALSE), 
  errorbars = list(show = FALSE)
)

scales <- list(
  fillcolor = list(palette = "identity", direction = NULL), 
  yaxis = list(limits = c(0, 1), nbreaks = 5, type = "percent", expand = NULL, droplines = TRUE)
)

legend <- list(
  show = FALSE, 
  title = NULL, 
  nrows = 1, 
  ncols = 1, 
  reverse = FALSE
)

vars <- list(
  xvar = "indicator_name", yvar = "group_cat_val", fillvar = "fillcolor"
)

facets <- list(
  type = "grid", 
  rows = "indicator_group2", 
  cols = "group_name", 
  scales = "free", 
  space = "free",
  drop_row_label = FALSE, 
  drop_col_label = FALSE, 
  add_dividers = FALSE
)

fig_flex(fig_data, vars, facets, figparams, scales, legend, labels, coord_flip = TRUE)


```
